### 2018-03-28 paper/paper.tex
論文paper.tex追加

\documentclass{sigchi}

% Use this section to set the ACM copyright statement (e.g. for
% preprints).  Consult the conference website for the camera-ready
% copyright statement.

% Copyright
\CopyrightYear{2016}
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}
% DOI
\doi{http://dx.doi.org/10.475/123_4}
% ISBN
\isbn{123-4567-24-567/08/06}
%Conference
\conferenceinfo{UIST'18,}{May 07--12, 2016, San Jose, CA, USA}
%Price
\acmPrice{\$15.00}

% Use this command to override the default ACM copyright statement
% (e.g. for preprints).  Consult the conference website for the
% camera-ready copyright statement.

%% HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP --
%% Please note you need to make sure the copy for your specific
%% license is used here!
% \toappear{
% Permission to make digital or hard copies of all or part of this work
% for personal or classroom use is granted without fee provided that
% copies are not made or distributed for profit or commercial advantage
% and that copies bear this notice and the full citation on the first
% page. Copyrights for components of this work owned by others than ACM
% must be honored. Abstracting with credit is permitted. To copy
% otherwise, or republish, to post on servers or to redistribute to
% lists, requires prior specific permission and/or a fee. Request
% permissions from \href{mailto:Permissions@acm.org}{Permissions@acm.org}. \\
% \emph{CHI '16},  May 07--12, 2016, San Jose, CA, USA \\
% ACM xxx-x-xxxx-xxxx-x/xx/xx\ldots \$15.00 \\
% DOI: \url{http://dx.doi.org/xx.xxxx/xxxxxxx.xxxxxxx}
% }

% Arabic page numbers for submission.  Remove this line to eliminate
% page numbers for the camera ready copy
% \pagenumbering{arabic}

% Load basic packages
\usepackage{balance}       % to better equalize the last page
\usepackage{graphics}      % for EPS, load graphicx instead 
\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
\usepackage{txfonts}
\usepackage{mathptmx}
% \usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage{color}
\usepackage{booktabs}
\usepackage{textcomp}

% Some optional stuff you might like/need.
\usepackage{microtype}        % Improved Tracking and Kerning
% \usepackage[all]{hypcap}    % Fixes bug in hyperref caption linking
\usepackage{ccicons}          % Cite your images correctly!
% \usepackage[utf8]{inputenc} % for a UTF8 editor only

% If you want to use todo notes, marginpars etc. during creation of
% your draft document, you have to enable the "chi_draft" option for
% the document class. To do this, change the very first line to:
% "\documentclass[chi_draft]{sigchi}". You can then place todo notes
% by using the "\todo{...}"  command. Make sure to disable the draft
% option again before submitting your final document.
\usepackage{todonotes}

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Bridging the Translation Gap with ExpandHelp}
\def\plainauthor{First Author, Second Author, Third Author,
  Fourth Author, Fifth Author, Sixth Author}
\def\emptyauthor{}
\def\plainkeywords{Authors' choice; of terms; separated; by
  semicolons; include commas, within terms only; required.}
\def\plaingeneralterms{Documentation, Standardization}

% llt: Define a global style for URLs, rather that the default one
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{
    \def\UrlFont{\sf}
  }{
    \def\UrlFont{\small\bf\ttfamily}
  }}
\makeatother
\urlstyle{leo}

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}

% Make sure hyperref comes last of your loaded packages, to give it a
% fighting chance of not being over-written, since its job is to
% redefine many LaTeX commands.
\definecolor{linkColor}{RGB}{6,125,233}
% \hypersetup{%
%   pdftitle={\plaintitle},
% % Use \plainauthor for final version.
% %  pdfauthor={\plainauthor},
%   pdfauthor={\emptyauthor},
%   pdfkeywords={\plainkeywords},
%   pdfdisplaydoctitle=true, % For Accessibility
%   bookmarksnumbered,
%   pdfstartview={FitH},
%   colorlinks,
%   citecolor=black,
%   filecolor=black,
%   linkcolor=black,
%   urlcolor=linkColor,
%   breaklinks=true,
%   hypertexnames=false
% }

% create a shortcut to typeset table headings
% \newcommand\tabhead[1]{\small\textbf{#1}}

% End of preamble. Here it comes the document.
\begin{document}

\title{\plaintitle}

\numberofauthors{3}
\author{%
%  \alignauthor{Leave Authors Anonymous\\
%    \affaddr{for Submission}\\
%    \affaddr{City, Country}\\
%    \email{e-mail address}}\\
  \alignauthor{Toshiyuki Masui
    \affaddr{Keio University}\\
    \affaddr{Fujisawa, Japan}\\
    \email{masui@pitecan.com}}\\
  \alignauthor{Jun Kato\\
    \affaddr{AIST}\\
    \affaddr{Tsukuba, Japan}\\
    \email{junkato}}\\
}

\maketitle

\begin{abstract}
  We introduce a flexible command translation system that can generate
  a complex complete command string from vague keywords
  given by the user.
  %
  % Although intuitive GUI are 
  % command-line interface (CLI) is stil widely used everywhere,
  %
  People use computers for various tasks that they want to perfer,
  but the language and vocabularies used for the task is usually completely different.
  When a user wants to ``make the room darker'',
  he should translate it to the real action like ``turn off the ceiling light'',
  and toggle the power switch or invoke a command like ``\texttt{\% iotctl ceilinglight 0}''.
  If the user is a Chinese speaker, he might have to translate his mind
  % ``使房黑暗'' into ``make the room darker'', and finally to \texttt{\% iotctl ceilinglight 0}.
  ``使房黒暗'' into ``make the room darker'', and finally to ``\texttt{\% iotctl ceilinglight 0}''.

  People in the world are always suffering from this kind of translation problem.
  Translation problems are serious for experienced Western computer users, but
  they are more serious for vast amount of people around the world.

  We propose a simple and general translation framework
  ``ExpandHelp'' that can be used in wide area of situation
  where translation is required, and
  show how the framework can be used
  by showing an example system ``\texttt{GitHelp}''
  that can help \texttt{git} users.

\end{abstract}

\category{H.5.m.}{Information Interfaces and Presentation
  (e.g. HCI)}{Miscellaneous} \category{See
  \url{http://acm.org/about/class/1998/} for the full list of ACM
  classifiers. This section is required.}{}{}

\keywords{\plainkeywords}

\section{Introduction}

\subsection{Title and Authors}

\subsection{Subsequent Pages}

\section{Acknowledgments}

\section{References Format}

% BALANCE COLUMNS
\balance{}

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{SIGCHI-Reference-Format}
\bibliography{sample}

\end{document}

### 2018-03-28 paper/paper.tex
...

@@
   We introduce a flexible command translation system that can generate
-  a complex complete command string from vague keywords
+  a complex command string from vague keywords
   given by the user.
@@
   %
-  People use computers for various tasks that they want to perfer,
-  but the language and vocabularies used for the task is usually completely different.
+  When people use computers to perform tasks,
+  there is usually a huge mismatch between the users' intention
+  and the required action.
+  % the language and vocabularies used for the task are completely different.
   When a user wants to ``make the room darker'',
-  he should translate it to the real action like ``turn off the ceiling light'',
-  and toggle the power switch or invoke a command like ``\texttt{\% iotctl ceilinglight 0}''.
-  If the user is a Chinese speaker, he might have to translate his mind
-  % ``使房黑暗'' into ``make the room darker'', and finally to \texttt{\% iotctl ceilinglight 0}.
-  ``使房黒暗'' into ``make the room darker'', and finally to ``\texttt{\% iotctl ceilinglight 0}''.
+  he should translate it to a real action like ``turn off the ceiling light''.
+  To do so,
+  he may have to toggle the wall switch
+  or issue a command like ``\texttt{\$ iot ceilinglight 0}''.
+  If the user is a Chinese speaker, he might have to translate his intention
+  ``使房黒暗'' into ``make the room darker'',
+  translate it to ``turn off the ceiling light'', 
+  and finally generate a command string like ``\texttt{\$ iot ceilinglight 0}''.
 
-  People in the world are always suffering from this kind of translation problem.
-  Translation problems are serious for experienced Western computer users, but
-  they are more serious for vast amount of people around the world.
-
+  People are perpetually suffering from such multi-level ``\textit{translation gaps}''.
+  Translation gaps exist even for experienced computer users, but
+  they are serious for vast amount of people around the world.
+  %
   We propose a simple and general translation framework
-  ``ExpandHelp'' that can be used in wide area of situation
-  where translation is required, and
-  show how the framework can be used
-  by showing an example system ``\texttt{GitHelp}''
-  that can help \texttt{git} users.
+  \textsf{ExpandHelp} that can be used in a wide area of situations
+  where such translation is required.
+  We show how our framework can be used
+  in the \textsf{GitHelp} system
+  with which user can easily generate complex \texttt{git} commands
+  from fragments of users' intentions.
 
@@
 \section{Introduction}
+
+When we use artifacts,
+we shoule translate our intentions into actions required for the artifacts.
+When we want to watch a movie, we may pick up a DVD disk, put it into a
+DVD player and push the play button, and set up other stuff.
+When we feel thirsty, we may go to the kitchen, pick up a glass, and
+turn the faucet on to fill the glass with water.
+
+% やりたいことが単純でも実際の操作は全然違ったり大変だったりすることが多い
+% 映画を見るためにネットサービスにアクセスするとかDVDを回すとか
+% 喉が乾いたら水道のところに行くとか冷蔵庫に行くとか
+% 人間社会ではそういう翻訳がとても多い
+% 現代社会ではさらに多い
+% 必要な作業が大体わかってる場合でもいろいろ文法や流儀があるので間違えずに動かすのは難しい
+% ネットサービスにアクセスするにはどうするんだっけ?
+% マニュアルやヘルプがあっても実際にそう有用なものではない
+% 誰も読まないし、うまくみつけられない
+% 映画を検索する方法は書いてあるかもしれないが、具体的に「ゴジラ」を見る方法は書いてない
+% 「ゴジラ 見る」だけで見たい
+% 外国語で考えている人はさらに大変で、コマンド実行できるまでには数段階の翻訳が必要になる
+% みんな脳内で翻訳しまくってることを理解するべき
+% 中国語引数のgitなんかないし
+% [* 以下の方針で解決できる]
+% やりたいことの[* 平易な表現と実行コマンドの組を用意]して[* 共有]しておいて、[* 簡単に検索/実行]できるようにする
+% 表現は[* 何語で書いてあってもかまわない]
+% ここけっこう強い制約な気がしていて、要は文字表現になってないと実行できないわけですよね。[Jun_Kato.icon]
+% [Chickenfoot]はブラウザ動作を録画して再生できるようにする研究でしたが、そういう、文字で表現しにくいdemonstrationをこの枠組みでは表現できないのが批判されそう（というか強い制約）だなと思いました。
+% http://up.csail.mit.edu/chickenfoot/
+% Chickenfootは、シンプルな表記でやりたいことを実現する枠組み(テキストベース)かと思ってました [増井俊之.icon]
+% Chickenfootを使ってたCoScripterが録画するシステムだったような
+% > In Chickenfoot, scripts are written in a superset of Javascript that includes special functions specific to web tasks.
+% つまり期待を膨らまさせすぎない（早い時点で、今回やってみるのはコマンドヘルプですよ、ということを明示する）のが大事そうです。
+% ナルホド [増井俊之.icon]
+% 文字表現(コマンド)じゃなきゃ駄目だというのはそのとおりで、あまり風呂敷を広げすぎない方が良いのかもしれませんね [増井俊之.icon]
+% 何語 というのは中国語でも日本語でも、という意味です
+% まぁ映画見るくらいならAmazon PrimeとかNetflixで該当作品検索してURLをブラウザで開くコードくらい書けそうですが。
+% そういうのが「翻訳」だと思うので、それをサポートしたいわけです [増井俊之.icon]
+% 映画を見たいということとAmazonとは何の関係もないわけで、何故PrimeだのNetflixだのを思い出せるのかということです
+% 思い出すにはかなり頭を使ってるハズ
+% 実際入会してたことを忘れてたり、Amazonで映画を見られることを知らなかったり
+% そういう便利スクリプトをいっぱい置けるシステムにするならそれはそれで。（でも時間切れになりそう）
+% translationというのは普通はテキストの変換を意味するから大丈夫かも
+% ちなみに同じことを何通りものコードで実行できる場合って全部が候補に出るわけですよね？ [Jun_Kato.icon]
+% 例えば映画作品見たいならAmazon PrimeとNetflix両方に作品があったりする
+% コマンドの例でいえば何をどの順番でパイプするかいろいろ選択肢がありうる
+% 全部出てくれると便利ですね（自分の知らなかったコマンド記法が学べたりする）
+% いろんな候補は出ます [増井俊之.icon]
+% 「Amazonでゴジラを見る」「Netflixでゴジラを見る」みたいに
+% コマンドの勉強になる とは思っています [増井俊之.icon]
+% そういう話は記述した方がいいかも
+% `@{2 days ago}`なんて記法を知ってる人は見たことなし [増井俊之.icon]
+% 今は自力で打てるようになった!
+% これを[* IMEみたいなインタフェースで利用する]
+% ちなIMEはアジアでは常識ね
+% [* データはWikiで共有しておいて誰でも追加/修正できる]
+% 自分のやり方を定義してもいい
 

### 2018-03-29 paper/paper.tex
...

@@
   To do so,
-  he may have to toggle the wall switch
+  he may have to ``toggle the wall switch''
   or issue a command like ``\texttt{\$ iot ceilinglight 0}''.
@@
 
-When we use artifacts,
+When we use modern artifacts,
 we shoule translate our intentions into actions required for the artifacts.
 When we want to watch a movie, we may pick up a DVD disk, put it into a
-DVD player and push the play button, and set up other stuff.
+DVD player, push the play button, and set up the audio and the monitor.
 When we feel thirsty, we may go to the kitchen, pick up a glass, and
 turn the faucet on to fill the glass with water.
+All the living creatures seem to be performing such translations
+between intentions and actions without difficulty, but
+in the modern world, people are suffering from
+serious gaps between what they want to do and what they have to do.
 
-% やりたいことが単純でも実際の操作は全然違ったり大変だったりすることが多い
-% 映画を見るためにネットサービスにアクセスするとかDVDを回すとか
-% 喉が乾いたら水道のところに行くとか冷蔵庫に行くとか
-% 人間社会ではそういう翻訳がとても多い
-% 現代社会ではさらに多い
-% 必要な作業が大体わかってる場合でもいろいろ文法や流儀があるので間違えずに動かすのは難しい
-% ネットサービスにアクセスするにはどうするんだっけ?
-% マニュアルやヘルプがあっても実際にそう有用なものではない
-% 誰も読まないし、うまくみつけられない
-% 映画を検索する方法は書いてあるかもしれないが、具体的に「ゴジラ」を見る方法は書いてない
-% 「ゴジラ 見る」だけで見たい
-% 外国語で考えている人はさらに大変で、コマンド実行できるまでには数段階の翻訳が必要になる
-% みんな脳内で翻訳しまくってることを理解するべき
-% 中国語引数のgitなんかないし
-% [* 以下の方針で解決できる]
+Even when people almost know what they have to do for what they want to do,
+it is often not easy to perform the task properly.
+Even when people know that they can watch a movie on the Internet,
+finding a movie and playing it is a difficult task for people without experiences.
+% even when detailed user manuals and documents exist.
+It would be nicer if they could watch a movie on the net
+just by showing a vague title or attributes of the movie
+in various languages.
+
+% We can use search engines to find clues for performing the tasks, but
+% it is not always easy for people in the world, since they may have
+% to use different languages to look for the information.
+
+We propose a command translationi system with which we can
+
 % やりたいことの[* 平易な表現と実行コマンドの組を用意]して[* 共有]しておいて、[* 簡単に検索/実行]できるようにする
 % 表現は[* 何語で書いてあってもかまわない]
-% ここけっこう強い制約な気がしていて、要は文字表現になってないと実行できないわけですよね。[Jun_Kato.icon]
-% [Chickenfoot]はブラウザ動作を録画して再生できるようにする研究でしたが、そういう、文字で表現しにくいdemonstrationをこの枠組みでは表現できないのが批判されそう（というか強い制約）だなと思いました。
-% http://up.csail.mit.edu/chickenfoot/
-% Chickenfootは、シンプルな表記でやりたいことを実現する枠組み(テキストベース)かと思ってました [増井俊之.icon]
-% Chickenfootを使ってたCoScripterが録画するシステムだったような
-% > In Chickenfoot, scripts are written in a superset of Javascript that includes special functions specific to web tasks.
-% つまり期待を膨らまさせすぎない（早い時点で、今回やってみるのはコマンドヘルプですよ、ということを明示する）のが大事そうです。
-% ナルホド [増井俊之.icon]
-% 文字表現(コマンド)じゃなきゃ駄目だというのはそのとおりで、あまり風呂敷を広げすぎない方が良いのかもしれませんね [増井俊之.icon]
-% 何語 というのは中国語でも日本語でも、という意味です
-% まぁ映画見るくらいならAmazon PrimeとかNetflixで該当作品検索してURLをブラウザで開くコードくらい書けそうですが。
-% そういうのが「翻訳」だと思うので、それをサポートしたいわけです [増井俊之.icon]
-% 映画を見たいということとAmazonとは何の関係もないわけで、何故PrimeだのNetflixだのを思い出せるのかということです
-% 思い出すにはかなり頭を使ってるハズ
-% 実際入会してたことを忘れてたり、Amazonで映画を見られることを知らなかったり
-% そういう便利スクリプトをいっぱい置けるシステムにするならそれはそれで。（でも時間切れになりそう）
-% translationというのは普通はテキストの変換を意味するから大丈夫かも
-% ちなみに同じことを何通りものコードで実行できる場合って全部が候補に出るわけですよね？ [Jun_Kato.icon]
 % 例えば映画作品見たいならAmazon PrimeとNetflix両方に作品があったりする

### 2018-03-31 paper/paper.tex
...

@@
 
-We propose a command translationi system with which we can
+We propose a command translation system with which users can get a complete
+command string
 
@@
 
-\subsection{Title and Authors}
+Contributions of this paper are as follows:
 
-\subsection{Subsequent Pages}
+\begin{enumerate}
+% 各種技術を組み合わせた翻訳支援というパラダイムの提案
+\item Introduction of a ``translation paradigm''
+\item IME-like command etnry system
+% やりたいことを実行するインタフェース (IME的なもの)
+\item Flexible dynamic search system based on RegExp (ExpandHelp)
+% そのための柔軟なインフラ (ExpandHelp)
+\item Data sharing infrastructure for the translation paradigm
+% 共有/編集しやすい正規表現DSLとそのインプリ(Scrapbox+)
+% \item これが唯一の解決法ではないが、こういう考え方がポピュラーになって欲しい
+\end{enumerate}
 
-\section{Acknowledgments}
+\section{Example}
+
+We have implemented ``GitHtlp'' that
 

### 2018-04-01 paper/paper.tex
...

@@
 \usepackage{mathptmx}
-% \usepackage[pdflang={en-US},pdftex]{hyperref}
+% \usepackage[pdflang={en-US},pdftex]{hyperref} なんかわからない
 \usepackage{color}
@@
 \author{%
-%  \alignauthor{Leave Authors Anonymous\\
-%    \affaddr{for Submission}\\
-%    \affaddr{City, Country}\\
-%    \email{e-mail address}}\\
   \alignauthor{Toshiyuki Masui
@@
 
-We propose a command translation system with which users can get a complete
-command string
+We propose a command translation system with which users can generate a complete
+command string.
+%
+We provide a database consisting of
+pairs of
+(1) the description of the task that users want to perform,
+and
+(2) the actual command string required by the system.
+(1) can be written using regular expressions in any language,
+
+For example, the database can include data like
+\texttt{\[ heya wo kuraku suru, \% iot ceiling 0 \]}.
 
@@
 
-We have implemented ``GitHtlp'' that
+We have implemented the ``GitHtlp'' system that can translate
+user' intentions into a correct \texttt{git} commands
+using the \textsf{ExpandHelp} framework.
+
+\paragraph{Entering a command}
+
+We assume that a user is using \texttt{bash} for developing a software system.
+
+When a
+
+\begin{figure}[b]
+  \includegraphics[width=8cm,bb=0 0 670 254]{figures/bash1.png}
+  \caption{Bash shell.}
+  \label{bash1}
+\end{figure}
+
+When the user wants to compare the latest \texttt{README.md} file with an
+older version, he tries to use \texttt{git} to show the difference.
+He may know that he can use the \texttt{git diff} command to do the
+conparison and invoke the following command,
+
+\begin{quotation}
+  \verb|$ git diff README.md|
+\end{quotation}
+
+but nothing happens, because this is not the right command
+to compare the latest version with older version.
+%
+More experienced user might use a command like the following,
+but it does not show anything either, because
+\verb|HEAD^^| means...
+
+\begin{quotation}
+  \verb|$ git diff HEAD^^ README.md|
+\end{quotation}
+
+Instead, the user can type \texttt{Cmd-Ctrl-G} to invoke
+\textsf{GitHelp}
+after typing
+\texttt{\$ git RE 2}.
+
+\begin{figure}[b]
+  \includegraphics[width=8cm,bb=0 0 1290 866]{figures/githelp1.png}
+  \caption{Invoking GitHelp.}
+  \label{bash1}
+\end{figure}
+
+Here, various command strings and descriptions are listed,
+one of which says ``.....'',
+which means that ``to compare README with two older verson.''
+%
+If the user thinks that that's what he wanted to do,
+he can select the entry by typing arrow keys and
+type the enter key.
 

### 2018-04-01 paper/paper.tex
...

@@
 % End of preamble. Here it comes the document.
+
+\def\GH{\textsf{GitHelp}}
+
 \begin{document}
@@
   We show how our framework can be used
-  in the \textsf{GitHelp} system
+  in the {\GH} system
   with which user can easily generate complex \texttt{git} commands
@@
 % 各種技術を組み合わせた翻訳支援というパラダイムの提案
-\item Introduction of a ``translation paradigm''
+\item Introduction of a ``translation paradigm'' to control a machine from vague specifications
 \item IME-like command etnry system
@@
 
-We have implemented the ``GitHtlp'' system that can translate
-user' intentions into a correct \texttt{git} commands
+We have implemented the \textsf{GitHtlp} system
+with which a user can translate his vague intention in various languages
+into a complete \texttt{git} commands
 using the \textsf{ExpandHelp} framework.
@@
 
-We assume that a user is using \texttt{bash} for developing a software system.
-
-When a
+We assume that the user is using \texttt{bash} for his software
+development activities.
 
@@
 He may know that he can use the \texttt{git diff} command to do the
-conparison and invoke the following command,
+conparison and invoke the following command like the following.
 
 \begin{quotation}
-  \verb|$ git diff README.md|
+  \begin{verbatim}
+    $ git diff README.md
+    $
+  \end{verbatim}
 \end{quotation}
 
-but nothing happens, because this is not the right command
+Nothing happens, because this is not the right command
 to compare the latest version with older version.
@@
 More experienced user might use a command like the following,
-but it does not show anything either, because
-\verb|HEAD^^| means...
+but it does not show anything either, because the version specification
+``\verb|HEAD^^|''
+points at a file included in the older ``commit'',
+and
 
@@
 
-Instead, the user can type \texttt{Cmd-Ctrl-G} to invoke
-\textsf{GitHelp}
-after typing
-\texttt{\$ git RE 2}.
+If {\GH} is installed,
+the user can type a special key (e.g. \texttt{Cmd-Ctrl-G}) to invoke {\GH}
+after typing ``\texttt{git RE 2}''.
 
@@
   \includegraphics[width=8cm,bb=0 0 1290 866]{figures/githelp1.png}
-  \caption{Invoking GitHelp.}
+  \caption{Invoking {\GH}.}
   \label{bash1}
@@
 
-Here, various command strings and descriptions are listed,
-one of which says ``.....'',
+Here, various candidate entries with
+descriptios and command strings are listed.
+One of the entries says ``.....'',
 which means that ``to compare README with two older verson.''

### 2018-04-02 paper/paper.tex
...

@@
 \def\GH{\textsf{GitHelp}}
+\def\SB{\textsf{Scrapbox}}
+\def\EH{\textsf{ExpandHelp}}
 
@@
 Nothing happens, because this is not the right command
-to compare the latest version with older version.
+to compare the latest version with one of the older versions.
 %
@@
 type the enter key.
+Then the command line is replaced by the correct command string
+that satisfies the user's need.
 
-\section{References Format}
+A description like ``2日前''(2 days ago) was also shown in the candidate list.
+This means that the user can use the same string ``\tettt{git RE 2}''
+for getting the README.md file of the day before yesterday.
+The command is ``$ git ... '@{2 days ago}''.
+Although such command options are very difficult to remember,
+users can do the same thing only by saying RE and 2.
 
-% BALANCE COLUMNS
-\balance{}
+\section{Implementation}
+
+{\EH} implementation
+
+\subsection{Translation}
+
+A powerful text-search mechanism called {\EH} is used in the
+background of {\GH}.
+
+{\EH} systemm is used in {\GH}.
+
+{\EH} is a general-purpose flexible help generation system
+that has the following characteristics.
+
+\begin{itemize}
+\item Use description-execution pairs for the translation
+\item Standard regular expression is used for the specification of the description
+\item The specification RegExp is expanded and filtered by the user's input string
+  real-time
+\end{itemize}
+
+An example of the desc-exec pair can be the following:
+
+\begin{verbatim}
+  (delete|remove) a (#{file})
+  /bin/rm $2
+\end{verbatim}
+
+``remove \verb|README.md|''
+into
+``\verb|rm README.md|
+
+First, the spec like \verb|#{file}| is expanded to a list of filenames like
+\verb+README.md|Makefile|test.c+,
+and the spec string becomes
+``\verb+(delete|remove) a file (README.md|Makefile|test.c)+''.
+Then this regular expression is expanded to all the possible string that match this regexp like
+\begin{verbatim}
+delete a file README.md
+remove a file README.md
+delete a file Makefile
+remove a file Makefile
+...
+\end{verbatim}
+
+And then all these strings are compared with the user's specification like
+``\verb|del REA|'',
+and if a matche is found,
+this is translated to
+``\verb|delete file README.md|''.
+
+If ``\verb|destroy|'' should also be used for the spec,
+the spec can be modified to 
+\verb+(delete|remove) a (#{file})+.
+
+Any kind of specs in any language can be used for the specification.
+For example,
+
+\begin{verbatim}
+  #{file}を(消す|消去する)
+  /bin/rm $1
+\end{verbatim}
+
+can be  used for Japanese users, who might want to delete
+one of the files by specifying ``消す''.
+(消す means 'delete' in Japanese).
+
+Approximate pattern matching
+
+\subsection{Sharing database on the Web}
+
+The translation data of {\GH} is written on {\SB} pages on the Web.
+{\SB} is a general-purpose flexible and powerful Wiki system where
+users can put any kind of data for sharing.
+For {\GH}, database entries like the following
+
+(Figure)
+
+Specs and command lines are specified with a special symbol, and
+all other documents can be written just like standard manuals and help documents.
+
+The document and the specs are written in the same document
+
+This is
+``literate programming'' style where
+source codes and documents are put in the same place.
+
+\section{Related Works}
+
+\subsection{IME}
+
+Text input systems for various languages are used widely in the world.
+They are called ``????''
+
+There are many
+
+\subsection{Command line completion}
+
+% コマンドライン補完
+% Emacs的な古いやつ、PBEのやつ、学習するやつ
+
+% Gitのcompletion
+
+\subsection{Smart IDEs}
+
+% 補完系IDEいろいろ
+% Miller方面いろいろ
+
+\subsection{Use cloud data for development}
+
+% 他人の情報利用する系
+% コード共有、コンパイルエラー共有
+
+\subsection{Using user forums}
+
+% Qiita, StackOverflow
+
+\subsection{Literate Programming}
+
+% 文芸的プログラミング
+% JavaDoc, Jupyter, Eve
+
+\section{Evaluation}
 

### 2018-04-03 paper/paper.tex
...

@@
 \def\EH{\textsf{ExpandHelp}}
+\long\def\tt#1{``\texttt{#1}''}
 
@@
   We propose a simple and general translation framework
-  \textsf{ExpandHelp} that can be used in a wide area of situations
+  {\EH} that can be used in a wide area of situations
   where such translation is required.
@@
 \section{Introduction}
+
+Online help systems are usually hard to use because of the
+vocabulary problem \cite{Furnas:1987:VPH:32206.32212}.
+
+People don't use online help
+\cite{Novick:2006:WDP:1166324.1166329}.
 
@@
 
-\section{Example}
+\section{Example: GitHelp}
 
-We have implemented the \textsf{GitHtlp} system
+We implemented the {\GH} system
 with which a user can translate his vague intention in various languages
-into a complete \texttt{git} commands
-using the \textsf{ExpandHelp} framework.
+into a complete \texttt{git} command
+using the {\EH} framework.
 
-\paragraph{Entering a command}
+\subsection{Entering a command}
 
@@
 
-\begin{figure}[b]
-  \includegraphics[width=8cm,bb=0 0 670 254]{figures/bash1.png}
-  \caption{Bash shell.}
-  \label{bash1}
-\end{figure}
+% \begin{figure}[h]
+%   \includegraphics[width=8cm,bb=0 0 670 254]{figures/bash1.png}
+%   \caption{Bash shell.}
+%   \label{bash1}
+% \end{figure}
 
@@
     $ git diff README.md
-    $
+    $ xxx
   \end{verbatim}
@@
 
-Nothing happens, because this is not the right command
-to compare the latest version with one of the older versions.
+Nothing happens, because this is not the approriate command
+to compare the latest version of \texttt{README.md}
+with older versions.
 %
@@
 ``\verb|HEAD^^|''
-points at a file included in the older ``commit'',
-and
+specifies a file included in the older ``commit'',
+and the following command only compares the \texttt{README.md}
+with the with the file included in the last commit, where
+\texttt{README.md} might be the same as the latest version.
 
@@
 the user can type a special key (e.g. \texttt{Cmd-Ctrl-G}) to invoke {\GH}
-after typing ``\texttt{git RE 2}''.
+after typing ``\verb|git RE |'' to see how he can do the job.
 
-\begin{figure}[b]
-  \includegraphics[width=8cm,bb=0 0 1290 866]{figures/githelp1.png}
+\begin{figure}[h]
+  % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
+  \includegraphics[width=10cm,bb=-100 -100 1190 766]{figures/githelp1.png}
   \caption{Invoking {\GH}.}
@@
 descriptios and command strings are listed.
-One of the entries says ``.....'',
-which means that ``to compare README with two older verson.''
+One of the entries says ``README.mdをひとつ前のバージョンと比較する'',
+which means that ``to compare README with the last verson.''
 %
 If the user thinks that that's what he wanted to do,
-he can select the entry by typing arrow keys and
-type the enter key.
+he can select the entry by moving the selection by typing arrow keys
+and type the enter key.
 Then the command line is replaced by the correct command string
@@
 
-A description like ``2日前''(2 days ago) was also shown in the candidate list.
-This means that the user can use the same string ``\tettt{git RE 2}''
+A description like ``1日前''(1 day ago) was also shown in the candidate list.
+This means that the user can use the same string ``\texttt{git RE 1}''
 for getting the README.md file of the day before yesterday.
-The command is ``$ git ... '@{2 days ago}''.
+The command is ``\verb|$ git ... '@{1 days ago}|''.
 Although such command options are very difficult to remember,
-users can do the same thing only by saying RE and 2.
+users can do the same thing only by saying \texttt{RE} and \texttt{1}.
 
@@
 
-\subsection{IME}
+\subsection{Input Methods}
 
-Text input systems for various languages are used widely in the world.
-They are called ``????''
+Text input systems for non-English languages are used widely in the world, and
+they are called as ``input methods'' (IMs).
 
-There are many
+\begin{figure}[b]
+  \includegraphics[width=8cm,bb=0 0 976 670]{figures/nyuuryoku-ime.png}
+  \caption{Example IM for Japanese text input.}
+  \label{bash1}
+\end{figure}
 
-\subsection{Command line completion}
+Many research and development on IMs have been performed for years, and
+people are using them all the time for entering text in their mother language.
 
-% コマンドライン補完
-% Emacs的な古いやつ、PBEのやつ、学習するやつ
+IMs are a kind of translation system that convert one
+expression (pronunciation, etc.) into a textual form of a language.
+In the above example, ``kanji'' will be translated to ``漢字''.
 
-% Gitのcompletion
+IMs are very popular especially in South-East Asian countries, and
+it is very common for people there to 
+use translation systems for using computers.
+
+\subsection{Text and code completion}
+
+On text editors an│shells,
+``text completion'' has been available for a long time.
+%
+When a user types the TAB key after typing \tt{la} on the Unix shell,
+\tt{latex}, \tt{latex}, and other commands are shown as candidates.
+When a user types \tt{ls RE} and types the TAB key,
+Unix shell checks the directory, find the \texttt{README.md} file, and
+replace the user's input with \tt{ls README.md}.
+This behavior is called ``text completion'', and many variations of
+this idea have been adopted in text editors and command line editors.
+
+User's history data can be used for 
+The Reactive Keyboard system\cite{ReactiveKeyboard}
+accumlates the user's command history and use the data
+for predicting the user's next command.
+Programing-by-Example (PBE) systems\cite{Cypher}\cite{Lieberman}.
+
+Gitsome(https://github.com/donnemartin/gitsome)
+helps \texttt{git} users by
+showing possible arguments and manuals on the Unix shell,
+just like {\GH}.
+The direction is alomost the same as {\GH}, but
+Gitsome does not support .....
 
 \subsection{Smart IDEs}
+
+Many smart IDEs for suggesting codes are proposed.
+
+賢い補完
+\cite{Little:2006:TKC:1166253.1166275}
+% キーワードの羅列からコマンドを作成するという考えはとても正しいと思うが、実装がいかがなものか?
+% キーワードぐらいは思い出せるプログラマが対象になっている
+% 「margin」とか「left」とかいう単語は思い出す必要がある
+% 「ちょっと字下げ」とか言っても駄目
+% キーワードが違ってると駄目?
+% いろいろズルをしてるようだ
+% [[ActiveDocument]]はよく出てくるので特別扱いしているとか
+% ステミングをしている
+% ``the'' ``to'' などは捨ててるのだろう
+% そもそもリカーシブな検索アルゴリズムにかなり無理がありそう
+% テンプレートを作るのは大変ではないのか?
+
+AnyCode\cite{Gvero:2015:SJE:2814270.2814295}
+% [anyCode]というシステム。自然言語キーワードを入力するとコードスニペットが表示される。
+% [[copy fileA fileB]]みたいなキーワードから[[FileUtil.copyFile(new File(fileA), new File(fileB))]]みたいなコード候補を生成する
+% [自然言語処理]を行なっている
+% [https://github.com/tihomirg/nlpcoder/tree/noola GitHub]
+% 曖昧検索はできない
+% 真面目に自然言語を入れる必要がある
+% `123`みたいなパラメタは使えるか?
+% 使えると思うが例には出てこない
+% コードの説明文は出ない?
+% FileUtil.copyFile(new File(fileA), new File(fileB)) と言われても、どちらが新しいファイルなのかわからない
+
+Active Code Completion\cite{Omar:2012:ACC:2337223.2337324}
+% [/ palette] と呼ばれるテンプレートを用意して[IDE]でのコード補完をサポートする
+% `getDefaultColor()` を定義したいとき`purple`と入力すると、それに対応した候補が提示されるとか
+% 普段使ってる環境で有益な候補が表示されると嬉しいだろうと言っている
+% [[コメント]]
+% [Jun Kato.icon]
+% > Active code completionも思い出しました。型ごとに適した入力インタフェースを出すコード補完インタフェースのnn提案です。確か。
+% [増井俊之.icon]
+% IDEでどういう機能が欲しいかサーベイして設計したことになっている
+% 色選択と正規表現のためのコード生成をサポートした例が紹介されている
+% 一般的な補完コマンド起動によって呼び出されるようだ
+% サポートウィンドウはHTML5で生成する
+% しかし両者とも[/palette]の作成はかなり大変である
+% 普通のユーザが作れるようなものではない
+% [* 作成がすごく大変]で、[* 特定のIDEでしか使えない]という問題があると思う
+
+Code Completion from Abbreviated\cite{Han:2009:CCA:1747491.1747530}
+% [HMM]を使って正しいコードを予測して提示する
+% `ch opn`みたいなテキトーな入力から`chooser.showOpenDialog()`みたいな正しいコードが候補に出る
+% コードデータベースを解析
+% [[コメント]]
+% [増井俊之.icon] 2018/3/23 18:53
+% コードのほんの一部を指定すると正しく予測されるというのは面白い
+% HMMってそういうのに使えるのね
+% しかし[* 関数名とか全然覚えていないときは使えないだろう]
+% [語彙問題]が解決できてない
+% だとすると高速入力の役にはたつが、何もかもわからない人をサポートはできない
+% 用例データが存在しない場合も使えない
+% [IDE]でしか使えない
+% [Cyrus Omar: Active code completion]で参照されている
 
@@
 
+\subsection{Context-based help}
+
 \subsection{Use cloud data for development}
+
+BluePrint \cite{Brandt:2010:EPI:1753326.1753402}
+%   サンプルコードをすぐ参照して利用できる[IDE]
+
+Bjorn\cite{Hartmann:2010:OPS:1753326.1753478}
+% 他人のヒストリを使ってコンパイルエラー対処法をサジェスト
 
@@
 
+参考文献にすることはないか
+
+Jupyter
+Eve
+
 % 文芸的プログラミング
@@
 \bibliographystyle{SIGCHI-Reference-Format}
-\bibliography{sample}
+\bibliography{paper}
 

### 2018-04-03 paper/paper.tex
...

@@
 % 各種技術を組み合わせた翻訳支援というパラダイムの提案
-\item Introduction of a ``translation paradigm'' to control a machine from vague specifications
+\item Introduction of ``\textit{translation paradigm}'' for
+  generating a correct instruction to a machine from
+  the user's vague intention
 \item IME-like command etnry system
@@
 $ git diff README.md
-    $ xxx
+$
 \end{verbatim}
@@
 
-\begin{figure}[b]
+\begin{figure}[h]
   \includegraphics[width=8cm,bb=0 0 976 670]{figures/nyuuryoku-ime.png}
-  \caption{Example IM for Japanese text input.}
+  \caption{An IM for Japanese text input.}
   \label{bash1}
@@
 just like {\GH}.
-The direction is alomost the same as {\GH}, but
-Gitsome does not support .....
+The goal of Git some is alomost the same as {\GH}, but
+Gitsome does not support ...
 

### 2018-04-03 paper/paper.tex
...

@@
 \cite{Novick:2006:WDP:1166324.1166329}.
+Twitterでのアンケート: 80\% が全然使わない
 
@@
 Gitsome(https://github.com/donnemartin/gitsome)
-helps \texttt{git} users by
-showing possible arguments and manuals on the Unix shell,
+helps \texttt{git} users by dynamically
+showing possible arguments and related manuals on the Unix shell,
 just like {\GH}.
-The goal of Git some is alomost the same as {\GH}, but
-Gitsome does not support ...
+The goal of Git some is alomost the same as {\GH} and we agree with its concept,
+but Gitsome does not support ...
 
@@
 
-% 補完系IDEいろいろ
-% Miller方面いろいろ
-
-\subsection{Context-based help}
-
-\subsection{Use cloud data for development}
+\subsection{Using cloud data for development}
+% 他人の情報利用する系
+% コード共有、コンパイルエラー共有
 
@@
 
-% 他人の情報利用する系
-% コード共有、コンパイルエラー共有
-
 \subsection{Using user forums}
@@
 
+Literate Programming\cite{Knuth}
+
 参考文献にすることはないか
 
+JavaDoc
 Jupyter
@@
 
-% 文芸的プログラミング
-% JavaDoc, Jupyter, Eve
+\section{Evaluation}
 
-\section{Evaluation}
+\section{Conclusion}
 

### 2018-04-03 paper/paper.tex
...

@@
 
-Online help systems are usually hard to use because of the
+When people want to perform a task using modern artifacts,
+people frequently find difficulty handling them properly.
+%
+Manuals and help systems are usually provided, but they are 
+usually hard to use because of the
 vocabulary problem \cite{Furnas:1987:VPH:32206.32212}.
+%
+People don't use online help systems\cite{Novick:2006:WDP:1166324.1166329}.
+Twitterでのアンケート: 80\% が全然使わない
+% https://gyazo.com/2dd525388cce34c916638f51bad386c7
 
-People don't use online help
-\cite{Novick:2006:WDP:1166324.1166329}.
-Twitterでのアンケート: 80\% が全然使わない
+やりたいと思ったことがすぐできればどれほど嬉しいことか
+そもそも検索や翻訳が必要なものであるならそれを楽にすればよい
 
-When we use modern artifacts,
+When we use artifacts,
 we shoule translate our intentions into actions required for the artifacts.

### 2018-04-03 paper/paper.tex
昔の論文からコピー中

@@
 
-\section{Related Works}
+\section{Related Work}
+
+\subsection{Intelligent help systems}
+
+There have been tremendous amount of researches on intelligent help systems\cite{Delisle:2002:UIH:606412.606415},
+but few number of projects seem to be going on these days,
+maybe because now we can use the Internet for getting intelligent help from
+real people.
+Information on the net is really rich these days, and we can easily
+find somebody who can answer questions intelligently.
+This is a very good news, but 
+asking many trivial questions on the net is not considered to be a
+good manner, and
+using a powerful and flexible local help system like ExpandHelp is
+preferable before asking other people.
 

### 2018-04-03 paper/paper.tex
...

@@
 %
-Manuals and help systems are usually provided, but they are 
-usually hard to use because of the
+Even when manuals and help systems are provided,
+they are usually hard to use because of the
 vocabulary problem \cite{Furnas:1987:VPH:32206.32212}.
@@
 When we use artifacts,
-we shoule translate our intentions into actions required for the artifacts.
+we should translate our vague intentions in our brain into actions required for the artifacts.
 When we want to watch a movie, we may pick up a DVD disk, put it into a

### 2018-04-03 paper/paper.tex
...

@@
 \usepackage{balance}       % to better equalize the last page
-\usepackage{graphics}      % for EPS, load graphicx instead 
+% \usepackage{graphics}      % for EPS, load graphicx instead 
+\usepackage{graphicx}      % for EPS, load graphicx instead 
 \usepackage[T1]{fontenc}   % for umlauts and other diaeresis
@@
 \long\def\tt#1{``\texttt{#1}''}
+\long\def\sf#1{``\textsf{#1}''}
 
@@
 
+Help documents used in ExpandHelp are provided as a set of data entries
+consisting of a regular expression which represents the help entry description
+and a corresponding command pattern.
+A description string is used to produce natural language texts
+which are easily understandable to users,
+while command patterns are used for invoking commands or calling library functions
+corresponding to the description.
+%
+For example, a help entry for finding a restaurant on the Web consists of
+the following data:
+
+\begin{quote}
+  description: \\
+  \texttt{Find a (Chinese|Korean|Vietnamese) restaurant \\  in (San Francisco|Chicago|New York) \\  on Yelp.com} \\
+  command: \\
+  \texttt{open 'http://www.yelp.com/search?\\  find\_loc=\$2\&find\_desc=\$1'}
+\end{quote}
+
+The first regular expression, the description part,
+is for generating texts like
+\sf{Find a Chinese restaurant in San Francisco}, 
+\sf{Find a Chinese restaurant in Chicago}, etc.,
+and the second part, command part,
+is used to generate a command for accessing \texttt{Yelp.com}.
+% Here, $1 and $2 corresponds to the matched pattern in the regular expression.
+In the first example, \sf{Chinese} and \sf{San Francisco}
+match the first and second parentheses of the regular expression, and
+these values are assigned to \texttt{\$1} and \texttt{\$2}
+for the command part, generating a URL
+\texttt{http://www.yelp. com/search?find\_loc=San\%20Francisco\&find\_desc= Chinese}.
+
+When the matched pattern like \sf{San Francisco}
+cannot be directly used in the command,
+parameters for the command can be put after the description string,
+separated by a TAB character.
+For example, when a number like ``\texttt{29247}'' should be used
+for checking the
+weather of San Francisco, we can describe the help entry like this:
+
+\begin{quote}\small
+ description: \\
+ \texttt{Check the weather of (San Francisco{\textbackslash}t29247| New York{\textbackslash}t23164)} \\
+ command: \\
+ \texttt{open 'http://local.msn.com/ten-day.aspx?\\eid=\$1'}
+\end{quote}
+
+Here, selecting a menu entry \sf{Check the weather of San Francisco}
+will produce a command
+\texttt{open 'http:{\slash}{\slash}local. msn.com{\slash}ten-day.aspx?eid=29247'}.
+
+-----------------------------------
+
 {\EH} is a general-purpose flexible help generation system
@@
 (消す means 'delete' in Japanese).
+
+\subsection*{Generating help menu entries}
+
+Finding appropriate entries from the huge help document space is performed in two steps.
+First, we parse the regular expression to
+generate a state transition diagram which represents all the strings represented
+in the regular expression.
+Second, we generate all the description strings by expanding the regular expression
+into a tree, and filter the generated strings by the pattern specified by the user.
+Efficient pattern matching is performed every time a new description text is generated,
+and only the best-matched descriptions are shown to the user as menu entries.
+We call this the ``\textit{generate-and-filter}'' technique,
+and we will describe the details later.
+% and we will describe the details of the algorithm later in this section.
+
+\subsection*{Phase 1: Generating a state transition diagram from a regular expression}
+
+Regular expressions are widely used for finding a pattern in a text string
+in modern programming languages and in the Unix environment.
+In ExpandHelp, we use a regular expression for
+generating various patterns of descriptions in a short form.
+For example, we use a short regular expression
+\tt{(remove|delete|erase) (data|file)}
+for representing expressions like
+\sf{remove data},
+\sf{erase file},
+etc.
+
+Converting a regular expression to a state transition machine is a straightforward task.
+When we have a regular expression
+\tt{Find a (Chinese|Korean|Vietnamese) restaurant in (San Francisco|Chicago|New York) on Yelp.com}, 
+we can parse the string and convert it into a state transition diagram
+shown in Figure \ref{statemachine1}.
+
+\begin{figure}[htb]
+\includegraphics[width=90mm,bb=0 0 573 124]{figures/statemachine.pdf}
+\caption{State transition diagram for finding a restaurant.}
+\label{statemachine1}
+\end{figure}
+
+% \includegraphics[height=12pt]{figures/startnode.pdf}
+% depicts the start node.
+
+By traversing the nodes and links in this state machine,
+we can generate the following description texts.
+
+\begin{quote}
+\small
+\textsf{Find a Chinese restaurant in San Francisco} \\
+\textsf{Find a Chinese restaurant in Chicago} \\
+...\\
+\textsf{Find a Vietnamese restaurant in New York}\\
+\end{quote}
+
+\subsection*{Phase 2: Generating texts from a state transition diagram}
+
+Using the state transition diagram shown in Figure \ref{statemachine1},
+ExpandHelp generates all the strings represented in the regular expressions,
+and filter them by the pattern provided by the user.
+
+We can generate texts from a state transition diagram by traversing nodes one by one.
+Starting at the start node (\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}})
+in Figure \ref{statemachine1},
+we can visit other nodes via edges and generate a tree of generated texts
+shown in Figure \ref{gentree1}.
+After visiting the initial node \raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}},
+the system generates a string \sf{Find a} and proceeds to the next node.
+In the second generation,
+the system can add \sf{Chinese}, \sf{Korean}, and \sf{Vietnamese}
+to \sf{Find a}, generating
+\sf{Find a Chinese},
+\sf{Find a Korean}, etc.
+The system can repeat finding edges from previously visited nodes,
+and eventually generates all the strings described above.
+Of course, it is impossible to generate all the strings
+from a regular expression like ``\texttt{(0|1)+}'' which represents infinite length of
+strings consisting of \texttt{0}s and \texttt{1}s, so the generation should be
+terminated at certain generation.
+
+\begin{figure}[htb]
+\includegraphics[width=85mm,bb=0 0 643 398]{figures/gentree1.pdf}
+\caption{Generating a text tree from a state transition machine.}
+\label{gentree1}
+\end{figure}
+
+\subsection{Generate-and-Filter}
+
+Generating all the texts in this way before finding matched strings is
+inefficient, because the amount of generated texts can easily become huge.
+Instead, the system performs the patter matching as soon as a text is generated,
+for saving time and memory.
+
+``Generate-and-test\footnote{
+  {\sf http:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Generate\_and\_test}
+}''
+technique is a simple and effective strategy
+used for solving puzzles and AI problems.
+Using this strategy, the ``8-Queen'' problem can be solved simply by
+generating all the possible queen layouts and checking if
+two or more queens are laid out on the same row, column, or diagonal line.
+Although this strategy is simple, the cost of
+generating all the possible solutions is prohibitive, since
+the solution space of the 8-Queen puzzle is $8^8 = 16,777,216$,
+which is not a small amount even for today's computers.
+
+To solve this problem,
+controlling the generation part from the testing part is usually effective.
+In the 8-Queen problem,
+whenever the testing part finds two queens in the same row or column,
+it can tell the generation part to
+give up current layout in the early stage and proceed to the next layout.
+
+Similarly in our case,
+it is not efficient to perform the matching operation
+after generating all the texts from the regular expression,
+and it is better to calculate the matching
+at the time of generating each text.
+We call it the ``\textit{generate-and-filter}'' strategy,
+and implemented the algorithm in ExpandHelp.
+Unlike simple puzzle problems where
+conditions are strict and finding one solution is enough,
+our goal is to find help description strings which
+fits the query pattern while allowing errors.
+For this goal,
+the system should perform approximate pattern matching
+without sacrificing processing speed.
+%
+We could implement flexible generate-and-filter by using a simple and efficient
+approximate pattern matching algorithm based on the ``shifter algorithm''.
 

### 2018-04-03 paper/paper.tex
...

--- 2018-04-03 paper/paper.tex
@@
 \def\EH{\textsf{ExpandHelp}}
-\long\def\tt#1{``\texttt{#1}''}
+\long\def\tt#1{\texttt{#1}}
+\long\def\sf#1{\textsf{#1}}
+\long\def\qtt#1{``\texttt{#1}''}
+\long\def\qsf#1{``\textsf{#1}''}
+\long\def\qit#1{``\textit{#1}''}
 
@@
   he may have to ``toggle the wall switch''
-  or issue a command like ``\texttt{\$ iot ceilinglight 0}''.
+  or issue a command like ``\tt{\$ iot ceilinglight 0}''.
   If the user is a Chinese speaker, he might have to translate his intention
@@
   translate it to ``turn off the ceiling light'', 
-  and finally generate a command string like ``\texttt{\$ iot ceilinglight 0}''.
+  and finally generate a command string like ``\tt{\$ iot ceilinglight 0}''.
 
@@
   in the {\GH} system
-  with which user can easily generate complex \texttt{git} commands
+  with which user can easily generate complex \tt{git} commands
   from fragments of users' intentions.
@@
 For example, the database can include data like
-\texttt{\[ heya wo kuraku suru, \% iot ceiling 0 \]}.
+\tt{\[ heya wo kuraku suru, \% iot ceiling 0 \]}.
 
@@
 with which a user can translate his vague intention in various languages
-into a complete \texttt{git} command
+into a complete \tt{git} command
 using the {\EH} framework.
@@
 
-We assume that the user is using \texttt{bash} for his software
+We assume that the user is using \tt{bash} for his software
 development activities.
@@
 
-When the user wants to compare the latest \texttt{README.md} file with an
-older version, he tries to use \texttt{git} to show the difference.
-He may know that he can use the \texttt{git diff} command to do the
+When the user wants to compare the latest \tt{README.md} file with an
+older version, he tries to use \tt{git} to show the difference.
+He may know that he can use the \tt{git diff} command to do the
 conparison and invoke the following command like the following.
@@
 Nothing happens, because this is not the approriate command
-to compare the latest version of \texttt{README.md}
+to compare the latest version of \tt{README.md}
 with older versions.
@@
 specifies a file included in the older ``commit'',
-and the following command only compares the \texttt{README.md}
+and the following command only compares the \tt{README.md}
 with the with the file included in the last commit, where
-\texttt{README.md} might be the same as the latest version.
+\tt{README.md} might be the same as the latest version.
 
@@
 If {\GH} is installed,
-the user can type a special key (e.g. \texttt{Cmd-Ctrl-G}) to invoke {\GH}
+the user can type a special key (e.g. \tt{Cmd-Ctrl-G}) to invoke {\GH}
 after typing ``\verb|git RE |'' to see how he can do the job.
@@
 A description like ``1日前''(1 day ago) was also shown in the candidate list.
-This means that the user can use the same string ``\texttt{git RE 1}''
+This means that the user can use the same string ``\tt{git RE 1}''
 for getting the README.md file of the day before yesterday.
@@
 Although such command options are very difficult to remember,
-users can do the same thing only by saying \texttt{RE} and \texttt{1}.
+users can do the same thing only by saying \tt{RE} and \tt{1}.
 
@@
 
-{\EH} implementation
+{\EH} search algorithm and database structure
 
-\subsection{Translation}
+% \subsection{Translation}
 
-A powerful text-search mechanism called {\EH} is used in the
-background of {\GH}.
+A powerful information retrieval mechanism called {\EH} is used in {\GH}.
 
-{\EH} systemm is used in {\GH}.
+Help data used in {\EH} are provided as a set of data entries
+consisting of a regular expression which represents the help entry description
+and a corresponding command pattern.
+A description string is used to produce natural language texts
+that are easily understandable by users,
+while command patterns are used for invoking commands or calling library functions
+corresponding to the description.
+%
+For example, a help entry for finding a restaurant on the Web consists of
+the following data:
+
+\begin{quote}
+  description: \\
+  \tt{Find a (Chinese|Korean|Vietnamese) restaurant \\  in (San Francisco|Chicago|New York) \\  on Yelp.com} \\
+  command: \\
+  \tt{open 'http://www.yelp.com/search?\\  find\_loc=\$2\&find\_desc=\$1'}
+\end{quote}
+
+The first regular expression, the description part,
+is for generating texts like
+\qsf{Find a Chinese restaurant in San Francisco}, 
+\qsf{Find a Chinese restaurant in Chicago}, etc.,
+and the second part, command part,
+is used to generate a command for accessing \tt{Yelp.com}.
+In the first example, \qsf{Chinese} and \qsf{San Francisco}
+match the first and second parentheses of the regular expression, and
+these values are assigned to \tt{\$1} and \tt{\$2}
+for the command part, generating a URL
+\tt{http://www.yelp.com/search?find\_loc=San\%20Francisco\&find\_desc=Chinese}.
+
+When the matched pattern like \qsf{San Francisco}
+cannot be directly used in the command,
+parameters for the command can be put after the description string,
+separated by a TAB character.
+For example, when a number like ``\tt{29247}'' should be used
+for checking the
+weather of San Francisco, we can describe the help entry like this:
+
+\begin{quote}\small
+ description: \\
+ \tt{Check the weather of (San Francisco{\textbackslash}t29247| New York{\textbackslash}t23164)} \\
+ command: \\
+ \tt{open 'http://local.msn.com/ten-day.aspx?\\eid=\$1'}
+\end{quote}
+
+Here, selecting a menu entry \qsf{Check the weather of San Francisco}
+will produce a command
+\tt{open 'http:{\slash}{\slash}local. msn.com{\slash}ten-day.aspx?eid=29247'}.
+
+\subsection{(section written for GitHelp)}
 
@@
 
-Approximate pattern matching
+\subsection{Generating help menu entries}
+
+Finding appropriate entries from the huge help document space is performed in two steps.
+First, we parse the regular expression to
+generate a state transition diagram that represents all the strings represented
+in the regular expression.
+Second, we generate all the description strings by expanding the regular expression
+into a tree, and filter the generated strings by the pattern specified by the user.
+Efficient pattern matching is performed every time a new description text is generated,
+and only the best-matched descriptions are shown to the user as menu entries.
+We call this the ``\textit{generate-and-filter}'' technique,
+and we will describe the details later.
+
+\subsubsection{Phase 1: Generating a state transition diagram from a regular expression}
+
+Regular expressions are widely used for finding patterns in text strings
+in modern programming languages and in the Unix environment.
+In {\EH}, we use regular expressions for
+generating various patterns of descriptions in a short form.
+For example, we use a short regular expression
+\qtt{(remove|delete|erase) (data|file)}
+for representing expressions like
+\qsf{remove data},\qsf{erase file}, etc.
+
+Converting a regular expression to a state transition machine is a straightforward task.
+When we have a regular expression
+\qtt{Find a (Chinese|Korean|Vietnamese) restaurant in (San Francisco|Chicago|New York) on Yelp.com}, 
+we can parse the string and convert it into a state transition diagram
+shown in Figure \ref{statemachine1}.
+
+\begin{figure}[htb]
+\includegraphics[width=90mm,bb=0 0 573 124]{figures/statemachine.pdf}
+\caption{State transition diagram for finding a restaurant.}
+\label{statemachine1}
+\end{figure}
+
+By traversing the nodes and links in this state machine,
+we can generate the following description texts.
+
+\begin{quote}
+\small
+\textsf{Find a Chinese restaurant in San Francisco} \\
+\textsf{Find a Chinese restaurant in Chicago} \\
+...\\
+\textsf{Find a Vietnamese restaurant in New York}\\
+\end{quote}
+
+\subsubsection{Phase 2: Generating texts from a state transition diagram}
+
+Using the state transition diagram shown in Figure \ref{statemachine1},
+{\EH} generates all the strings represented in the regular expressions,
+and filter them by the pattern provided by the user.
+
+We can generate texts from a state transition diagram by traversing nodes one by one.
+Starting at the start node
+(\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}})
+in Figure \ref{statemachine1},
+we can visit other nodes via edges and generate a tree of generated texts
+shown in Figure \ref{gentree1}.
+After visiting the initial node
+\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}},
+the system generates a string \qsf{Find a} and proceeds to the next node.
+In the second generation,
+the system can add \qsf{Chinese}, \qsf{Korean}, and \qsf{Vietnamese}
+to \qsf{Find a}, generating
+\qsf{Find a Chinese}, \qsf{Find a Korean}, etc.
+The system can repeat finding edges from previously visited nodes,
+and eventually generates all the strings described above.
+Of course, it is impossible to generate all the strings
+from a regular expression like ``\tt{(0|1)+}'' which represents infinite length of
+strings consisting of \tt{0}s and \tt{1}s, so the generation should be
+terminated at certain generation.
+
+\begin{figure}[htb]
+\includegraphics[width=85mm,bb=0 0 643 398]{figures/gentree1.pdf}
+\caption{Generating a text tree from a state transition machine.}
+\label{gentree1}
+\end{figure}
+
+\subsection{Generate-and-Filter}
+
+Generating all the texts in this way before finding matched strings is
+inefficient, because the amount of generated texts can easily become huge.
+Instead, the system performs the patter matching as soon as a text is generated,
+for saving time and memory.
+
+``Generate-and-test\footnote{
+  {\sf http:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Generate\_and\_test}
+}''
+technique is a simple and effective strategy
+used for solving puzzles and AI problems.
+For example,
+the ``8-Queen'' problem can be solved simply by
+generating all the possible queen layouts and checking if
+two or more queens are laid out on the same row, column, or diagonal line.
+Although this strategy is simple, the cost of
+generating all the possible solutions is prohibitive, since
+the solution space of the 8-Queen puzzle is $8^8 = 16,777,216$,
+which is not a small amount even for today's computers.
+
+To solve this problem,
+controlling the generation part from the testing part is effective.
+In the 8-Queen problem,
+whenever the testing part finds two queens in the same row or column,
+it can tell the generation part to
+give up current layout in the early stage and proceed to the next layout.
+
+Similarly in our case,
+it is not efficient to perform the matching operation
+after generating all the texts from the regular expression,
+and it is better to calculate the matching
+at the time of generating each text.
+We call it the \qit{generate-and-filter} strategy,
+and implemented the algorithm in {\EH}.
+Unlike simple puzzle problems where
+conditions are strict and finding one solution is enough,
+our goal is to find help description strings
+that fits the query pattern while allowing errors.
+For this goal,
+the system should perform approximate pattern matching
+without sacrificing processing speed.
+%
+We could implement flexible generate-and-filter by using a simple and efficient
+approximate pattern matching algorithm based on the ``shifter algorithm''.
+
+\subsection{Approximate pattern matching by shifter algorithm}
+
+簡潔に書けるか?
 
@@
 
-The translation data of {\GH} is written on {\SB} pages on the Web.
-{\SB} is a general-purpose flexible and powerful Wiki system where
-users can put any kind of data for sharing.
+The data used in {\GH} are represented as {\SB} documents.
+%
+{\SB} is a general-purpose flexible Wiki system for
+any kind of data sharing.
+{\SB} users can edit the contents of Wiki pages directly
+on Web browsers just like text editors, and simple
+markup symbols can be used just like MarkDown\footnote{markdown}
+and other markup languages.
+
 For {\GH}, database entries like the following
 
-(Figure)
+% \begin{figure}[htb]
+% \begin{verbatim}
+% \end{verbatim}
+% \centerline{\includegraphics[width=40mm]{figures/xxxxx}}
+% \caption{ssss}
+% \label{xxxxx}
+% \end{figure}
 
-Specs and command lines are specified with a special symbol, and
-all other documents can be written just like standard manuals and help documents.
+This page describes the usage of \qtt{git diff}, and
+the page contains command specifications in {\EH} format
+in addition to the description of the command.
+%
+% Specs and command lines are specified with a special symbol, and
+% all other documents can be written just like standard manuals and help documents.
 
-The document and the specs are written in the same document
+Although usage examples are often shown on Unix man pages,
+they cannot be used as the database of online help system.
+On the other hand,
+a {\SB} document contains both the manual page and the help database
+at the same place.
+%
+This strategy is similar to the
+``Literate Programming'' style,
+where source codes and documents are put in the same document.
 
-This is
-``literate programming'' style where
-source codes and documents are put in the same place.
+Also, since the database is on the Wiki page, any member of the
+Wiki can correct the document or add additional {\GH} specifications.
+When a user could not get a good support from {\GH}, he can add
+{\EH} specifications to the {\SB} document himself
+so that he and other people can get an appropriate support next time.
 
@@
 %
-When a user types the TAB key after typing \tt{la} on the Unix shell,
-\tt{latex}, \tt{latex}, and other commands are shown as candidates.
-When a user types \tt{ls RE} and types the TAB key,
-Unix shell checks the directory, find the \texttt{README.md} file, and
-replace the user's input with \tt{ls README.md}.
+When a user types the TAB key after typing \qtt{la} on the Unix shell,
+\qtt{latex}, \qtt{latex}, and other commands are shown as candidates.
+When a user types \qtt{ls RE} and types the TAB key,
+Unix shell checks the directory, find the \tt{README.md} file, and
+replace the user's input with \qtt{ls README.md}.
 This behavior is called ``text completion'', and many variations of
@@
 Gitsome(https://github.com/donnemartin/gitsome)
-helps \texttt{git} users by dynamically
+helps \tt{git} users by dynamically
 showing possible arguments and related manuals on the Unix shell,

### 2018-04-04 paper/paper.tex
...

@@
+% compare current (README.md|index.html) with the file from 2 versions ago
+% compare (README.md|index.html) with the one from (1|2|3|4) versions before
+% compare current (README.md|index.html) with that from  ([0-9]+)-days ago
+
 \documentclass{sigchi}
@@
 % Copyright
-\CopyrightYear{2016}
+\CopyrightYear{2018}
 %\setcopyright{acmcopyright}
@@
 \long\def\tt#1{\texttt{#1}}
+\long\def\stt#1{\texttt{\small{#1}}}
 \long\def\sf#1{\textsf{#1}}
-\long\def\qtt#1{``\texttt{#1}''}
-\long\def\qsf#1{``\textsf{#1}''}
+\long\def\ssf#1{\textsf{\small{#1}}}
+\long\def\qtt#1{``\tt{#1}''}   % quote tt
+\long\def\sqtt#1{``\stt{#1}''} % smal quote tt
+\long\def\qsf#1{``\sf{#1}''}
+\long\def\sqsf#1{``\ssf{#1}''}
 \long\def\qit#1{``\textit{#1}''}
@@
   the user's vague intention
-\item IME-like command etnry system
-% やりたいことを実行するインタフェース (IME的なもの)
 \item Flexible dynamic search system based on RegExp (ExpandHelp)
 % そのための柔軟なインフラ (ExpandHelp)
+\item IME-like command etnry interface
+% やりたいことを実行するインタフェース (IME的なもの)
 \item Data sharing infrastructure for the translation paradigm
@@
 
-There have been tremendous amount of researches on intelligent help systems\cite{Delisle:2002:UIH:606412.606415},
+There have been many researches on intelligent help systems\cite{Delisle:2002:UIH:606412.606415},
 but few number of projects seem to be going on these days,
 maybe because now we can use the Internet for getting intelligent help from
-real people.
-Information on the net is really rich these days, and we can easily
+real people,
+either by searching Web pages or 
+by asking in user forums like StackOverflow\footnote{stackoverflow}.
+Information on the net is rich these days, and we can easily
 find somebody who can answer questions intelligently.
-This is a very good news, but 
+This is a good news, but 
 asking many trivial questions on the net is not considered to be a
 good manner, and
-using a powerful and flexible local help system like ExpandHelp is
+using a powerful and flexible local help system like {\EH} is
 preferable before asking other people.
@@
 
-Text input systems for non-English languages are used widely in the world, and
-they are called as ``input methods'' (IMs).
+Text input systems for non-English languages are widely used
+in the world,
+and they are called as ``Input Methods'' (IMs).
+%
+Many research and development on IMs have been going on for years, and
+people are using them every day for entering texts in their mother language.
 
@@
 
-Many research and development on IMs have been performed for years, and
-people are using them all the time for entering text in their mother language.
+IMs are one form of translation systems that convert one
+expression (pronunciation, character shape, etc.)
+into a textual form of a language.
+In the above example, the pronunciation ``kanji''
+is used for getting ``漢字''.
 
-IMs are a kind of translation system that convert one
-expression (pronunciation, etc.) into a textual form of a language.
-In the above example, ``kanji'' will be translated to ``漢字''.
-
-IMs are very popular especially in South-East Asian countries, and
-it is very common for people there to 
+IMs are very popular in the world these days,
+and it is very common for people to 
 use translation systems for using computers.
+Using an additional translation system like {\GH} is ...
 
@@
 
-On text editors an│shells,
+On text editors and Unix shells,
 ``text completion'' has been available for a long time.
@@
 This behavior is called ``text completion'', and many variations of
-this idea have been adopted in text editors and command line editors.
+this idea have been proposed and adopted in text editors and command line editors.
 
-User's history data can be used for 
-The Reactive Keyboard system\cite{ReactiveKeyboard}
+User's history data can also be used for the completion function.
+The Reactive Keyboard\cite{ReactiveKeyboard}
 accumlates the user's command history and use the data
-for predicting the user's next command.
-Programing-by-Example (PBE) systems\cite{Cypher}\cite{Lieberman}.
+for predicting the user's next input.
 
-Gitsome(https://github.com/donnemartin/gitsome)
-helps \tt{git} users by dynamically
-showing possible arguments and related manuals on the Unix shell,
+% Programing-by-Example (PBE) systems\cite{Cypher}\cite{Lieberman}.
+
+Gitsome\footnote{\textsf{https:{\slash}{\slash}github.com{\slash}donnemartin{\slash}gitsome}}
+helps \tt{git} users by
+dynamically showing possible arguments and related manuals on the Unix shell,
 just like {\GH}.
-The goal of Git some is alomost the same as {\GH} and we agree with its concept,
+The goal of Gitsome is alomost the same as {\GH} and we agree with its concept,
 but Gitsome does not support ...
@@
 
-Many smart IDEs for suggesting codes are proposed.
+Many smart IDEs for suggesting codes have been proposed resently.
 
-賢い補完
-\cite{Little:2006:TKC:1166253.1166275}
+% 賢い補完
+Little's system\cite{Little:2006:TKC:1166253.1166275}
+generates a complete JavaScript code snippet from keyword fragments.
+For example,
+\qtt{ActiveDocument .PageSetup .LeftMargin = InchesToPoints(2)}
+can be generated from keywords like
+\qsf{left},
+\qsf{margin},
+\qsf{4}, and
+\qsf{inches}.
+The system generates the code using a template database and heuristics
+for the target system.
+It is useful for a special environment, but
+users of the system cannot modify the algorithm or the database
+even when appropriate suggestions cannot be give by the system.
+
 % キーワードの羅列からコマンドを作成するという考えはとても正しいと思うが、実装がいかがなものか?
@@
 
-AnyCode\cite{Gvero:2015:SJE:2814270.2814295}
+% https://www.youtube.com/watch?v=93vZAmLyOQY
+AnyCode\cite{Gvero:2015:SJE:2814270.2814295} is another system
+that generates a complete code snippet from the user's
+input in natural language.
+AnyCode can handle synonyms like ``make'' == ``create'',
+曖昧検索はできず、かなりキーワードを指定する必要はある
+
 % [anyCode]というシステム。自然言語キーワードを入力するとコードスニペットが表示される。
@@
 Active Code Completion\cite{Omar:2012:ACC:2337223.2337324}
+is another code completion system for the Eclipse IDE.
+A database called \textit{palette} are used for code completion and coding support
+for Java classes.
+When a user wants to write a code for drawing a rectangle in purple,
+the user should just tell ``purple'' to the system,
+and the system shows the user a color selection window
+as well as the Java code for drawing a purple rectangle.
+This is a useful feature for the user to write a code including selecting
+a color, but paletts are difficult to create, and should be provided
+as IDE plugins.
 % [/ palette] と呼ばれるテンプレートを用意して[IDE]でのコード補完をサポートする
@@
 
-Code Completion from Abbreviated\cite{Han:2009:CCA:1747491.1747530}
+Han's Abbreviation Completion system\cite{Han:2009:CCA:1747491.1747530}
+can generate a code snippet from abbreviation strings give by the user.
+For example, a snippet like \qtt{chooser. showOpenDialog()}
+can be generated from the keyword
+\qsf{ch} and\qsf{opn}, using the code database and HMM.
+It can be very useful as a shorthand for handling long names,
+but users should have a vague knowledge about the correct names
+(e.g. \qtt{chooser}, \qtt{dialog}),
+and large code example corpus should exist before
+
 % [HMM]を使って正しいコードを予測して提示する
@@
 \subsection{Using cloud data for development}
+
 % 他人の情報利用する系
@@
 
-BluePrint \cite{Brandt:2010:EPI:1753326.1753402}
+Many systems support sharing users' development experiences on the web so that
+they can be used on the developers' IDE.
+
+Using BluePrint\cite{Brandt:2010:EPI:1753326.1753402}
+as a plugin for Adobe Flex Builder,
+users can search sample codes from the Web and use it immediately
+as
+
 %   サンプルコードをすぐ参照して利用できる[IDE]
 
-Bjorn\cite{Hartmann:2010:OPS:1753326.1753478}
-% 他人のヒストリを使ってコンパイルエラー対処法をサジェスト
+HelpMeOut\cite{Hartmann:2010:OPS:1753326.1753478} tells users
+how to handle compile errors,
+based on the people's experiences of handling compile errors.
 
-\subsection{Using user forums}
+%= 他人のヒストリを使ってコンパイルエラー対処法をサジェスト
 
+% \subsection{Using user forums}
+% 
 % Qiita, StackOverflow
+%
 

### 2018-04-04 paper/paper.tex
...

@@
 % compare current (README.md|index.html) with that from  ([0-9]+)-days ago
+
+% 部屋を暗くする
+% make the room darker 
+% iot ......
 
@@
   If the user is a Chinese speaker, he might have to translate his intention
-  ``使房黒暗'' into ``make the room darker'',
-  translate it to ``turn off the ceiling light'', 
-  and finally generate a command string like ``\tt{\$ iot ceilinglight 0}''.
+  % ``使房黒暗'' into ``make the room darker'',
+  ``房間暗一点'' into ``make the room darker'',
+  ``turn off the ceiling light'', 
+  ``toggle the wall switch'',
+  and finally to a command like ``\tt{\$ iot ceilinglight 0}''.
 
@@
   We propose a simple and general translation framework
-  {\EH} that can be used in a wide area of situations
+  {\EH} that can be used in various situations
   where such translation is required.
@@
   from fragments of users' intentions.
-
 \end{abstract}
@@
 Even when manuals and help systems are provided,
-they are usually hard to use because of the
-vocabulary problem \cite{Furnas:1987:VPH:32206.32212}.
+people don't use them\cite{Novick:2006:WDP:1166324.1166329}
+partly because of the vocabulary problem\cite{Furnas:1987:VPH:32206.32212}.
 %
-People don't use online help systems\cite{Novick:2006:WDP:1166324.1166329}.
-Twitterでのアンケート: 80\% が全然使わない
+% Twitterでのアンケート: 80\% が全然使わない
 % https://gyazo.com/2dd525388cce34c916638f51bad386c7
-
-やりたいと思ったことがすぐできればどれほど嬉しいことか
-そもそも検索や翻訳が必要なものであるならそれを楽にすればよい
-
-When we use artifacts,
-we should translate our vague intentions in our brain into actions required for the artifacts.
+% 
+% やりたいと思ったことがすぐできればどれほど嬉しいことか
+% そもそも検索や翻訳が必要なものであるならそれを楽にすればよい
+%
+We should translate our vague intentions in our brain into actions required for the artifacts.
 When we want to watch a movie, we may pick up a DVD disk, put it into a
@@
 turn the faucet on to fill the glass with water.
-All the living creatures seem to be performing such translations
+All the living creatures are performing such translations
 between intentions and actions without difficulty, but
@@
 
-Even when people almost know what they have to do for what they want to do,
-it is often not easy to perform the task properly.
+Even when people vaguely know what they have to do for what they want to do,
+it is often not easy for them to perform the task properly.
 Even when people know that they can watch a movie on the Internet,
 finding a movie and playing it is a difficult task for people without experiences.
-% even when detailed user manuals and documents exist.
 It would be nicer if they could watch a movie on the net
@@
 
-We propose a command translation system with which users can generate a complete
+We propose a simple, flexible and powerful
+command translation framework with which users can generate a complete
 command string.
@@
 
-We implemented the {\GH} system
+We implemented the ``{\GH}'' system
 with which a user can translate his vague intention in various languages
@@
 
-A powerful information retrieval mechanism called {\EH} is used in {\GH}.
+A powerful information retrieval mechanism ``{\EH}'' is used in {\GH}.
 
@@
   description: \\
-  \tt{Find a (Chinese|Korean|Vietnamese) restaurant \\  in (San Francisco|Chicago|New York) \\  on Yelp.com} \\
+  \stt{Find a (Chinese|Korean|Vietnamese) restaurant \\  in (San Francisco|Chicago|New York) \\  on Yelp.com} \\
   command: \\
-  \tt{open 'http://www.yelp.com/search?\\  find\_loc=\$2\&find\_desc=\$1'}
+  \stt{open 'http://www.yelp.com/search?\\  find\_loc=\$2\&find\_desc=\$1'}
 \end{quote}
@@
 
-The data used in {\GH} are represented as {\SB} documents.
+The data used in {\GH} are represented as ``{\SB}'' documents.
 %
-{\SB} is a general-purpose flexible Wiki system for
-any kind of data sharing.
+{\SB} is a general-purpose real-time Wiki system for data sharing.
 {\SB} users can edit the contents of Wiki pages directly
-on Web browsers just like text editors, and simple
-markup symbols can be used just like MarkDown\footnote{markdown}
+on Web browsers just like text editors,
+using simple markup symbols similar to MarkDown\footnote{markdown}
 and other markup languages.

### 2018-04-05 paper/paper.tex
...

@@
 \long\def\tt#1{\texttt{#1}}
-\long\def\stt#1{\texttt{\small{#1}}}
+\long\def\stt#1{\texttt{\fontsize{9pt}{0pt}\selectfont{#1}}}
 \long\def\sf#1{\textsf{#1}}
-\long\def\ssf#1{\textsf{\small{#1}}}
+\long\def\ssf#1{\textsf{\fontsize{9pt}{0pt}\selectfont{#1}}}
 \long\def\qtt#1{``\tt{#1}''}   % quote tt
@@
   % the language and vocabularies used for the task are completely different.
-  When a user wants to ``make the room darker'',
-  he should translate it to a real action like ``turn off the ceiling light''.
-  To do so,
-  he may have to ``toggle the wall switch''
-  or issue a command like ``\tt{\$ iot ceilinglight 0}''.
-  If the user is a Chinese speaker, he might have to translate his intention
-  % ``使房黒暗'' into ``make the room darker'',
-  ``房間暗一点'' into ``make the room darker'',
-  ``turn off the ceiling light'', 
-  ``toggle the wall switch'',
-  and finally to a command like ``\tt{\$ iot ceilinglight 0}''.
-
-  People are perpetually suffering from such multi-level ``\textit{translation gaps}''.
+  %
+  For example, when a Chinese person wants to ``房間暗一点'' (make the room darker),
+  % he may have to translate his intention into an English expression ``make the room darker'',
+  he may have to find that he should ``turn off the ceiling light'' for the task,
+  translate it to a required action ``toggle the wall switch''
+  or a command like ``\tt{\$ iot clight 0}''.
+  %
+  % When a user wants to ``make the room darker'',
+  % he should translate it to a real action like ``turn off the ceiling light''.
+  % To do so,
+  % he may have to ``toggle the wall switch''
+  % or issue a command like ``\tt{\$ iot ceilinglight 0}''.
+  % If the user is a Chinese speaker, he might have to translate his intention
+  % ``房間暗一点'' into ``make the room darker'',
+  % ``turn off the ceiling light'', 
+  % ``toggle the wall switch'',
+  % and finally to a command like ``\tt{\$ iot ceilinglight 0}''.
+  %
+  There is a huge gap between ``房間暗'' and ``\tt{\$ iot clight 0}'', and
+  people are perpetually suffering from such multi-level ``\textit{translation gaps}''.
   Translation gaps exist even for experienced computer users, but
@@
 We propose a simple, flexible and powerful
-command translation framework with which users can generate a complete
-command string.
+translation framework with which users can generate a complete
+command string from fragments of users' vague intentions.
 %
-We provide a database consisting of
-pairs of
-(1) the description of the task that users want to perform,
+We provide a database consisting of pairs of
+the description of the task that users want to perform (e.g. 房間暗一点)
 and
-(2) the actual command string required by the system.
-(1) can be written using regular expressions in any language,
-
-For example, the database can include data like
-\tt{\[ heya wo kuraku suru, \% iot ceiling 0 \]}.
+the actual command string required by the system (e.g. \tt{\$ iot clight 0}).
+Descriptions can be written in any natural language using regular expressions
+and the database on the Wiki pages can be edited by any user
+who wants to improve the database.
 
@@
 \item Introduction of ``\textit{translation paradigm}'' for
-  generating a correct instruction to a machine from
-  the user's vague intention
-\item Flexible dynamic search system based on RegExp (ExpandHelp)
+  generating a correct instruction to an artifact from
+  the user's vague intention in natural language.
+\item General-purpose flexible dynamic search system based on regular expressions.
 % そのための柔軟なインフラ (ExpandHelp)
-\item IME-like command etnry interface
+% \item IME-like command etnry interface
 % やりたいことを実行するインタフェース (IME的なもの)
-\item Data sharing infrastructure for the translation paradigm
+\item Data sharing infrastructure for the above strategy.
 % 共有/編集しやすい正規表現DSLとそのインプリ(Scrapbox+)
@@
 
-We implemented the ``{\GH}'' system
+We implemented the {\GH} system
 with which a user can translate his vague intention in various languages
@@
 
-We assume that the user is using \tt{bash} for his software
+We assume that the user uses \tt{bash} for his software
 development activities.
@@
 
-When the user wants to compare the latest \tt{README.md} file with an
-older version, he tries to use \tt{git} to show the difference.
-He may know that he can use the \tt{git diff} command to do the
-conparison and invoke the following command like the following.
-
-\begin{quotation}
-\begin{verbatim}
-$ git diff README.md
-$
-\end{verbatim}
-\end{quotation}
-
-Nothing happens, because this is not the approriate command
-to compare the latest version of \tt{README.md}
-with older versions.
-%
-More experienced user might use a command like the following,
-but it does not show anything either, because the version specification
+When a user wants to compare the latest \tt{README.md} file
+with the same file from 2 versions before,
+he might try to use \tt{git} with an argument
 ``\verb|HEAD^^|''
-specifies a file included in the older ``commit'',
-and the following command only compares the \tt{README.md}
-with the with the file included in the last commit, where
-\tt{README.md} might be the same as the latest version.
+for specifying an old version.
 
@@
   \verb|$ git diff HEAD^^ README.md|
+  \par
+  \verb|$|
 \end{quotation}
 
+Nothing happens here because
+\verb|HEAD^^|
+specifies a file included in the older commit,
+and the command above only compares the \tt{README.md}
+with the file included in an old commit, where
+\tt{README.md} might be the same as the latest version.
+
 If {\GH} is installed,
-the user can type a special key (e.g. \tt{Cmd-Ctrl-G}) to invoke {\GH}
-after typing ``\verb|git RE |'' to see how he can do the job.
+the user can type a special shortcut key
+% (e.g. \tt{Cmd-Ctrl-G})
+to invoke {\GH} after typing ``\verb|git RE 2|'' to see how he can do the job.
 
@@
   % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
-  \includegraphics[width=10cm,bb=-100 -100 1190 766]{figures/githelp1.png}
+  % \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
+  \includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp1.png}
   \caption{Invoking {\GH}.}
@@
 descriptios and command strings are listed.
-One of the entries says ``README.mdをひとつ前のバージョンと比較する'',
-which means that ``to compare README with the last verson.''
+One of the entries says ``README.mdをふたつ前のバージョンと比較する'',
+which means ``to compare \tt{README.md} with the one from 2 versions before.''
 %
-If the user thinks that that's what he wanted to do,
-he can select the entry by moving the selection by typing arrow keys
+If the user thinks that that's what he wants to do,
+he can select the entry by selecting it by typing arrow keys
 and type the enter key.
-Then the command line is replaced by the correct command string
+Then the user's input string is replaced by the right command string
 that satisfies the user's need.
 
-A description like ``1日前''(1 day ago) was also shown in the candidate list.
-This means that the user can use the same string ``\tt{git RE 1}''
-for getting the README.md file of the day before yesterday.
-The command is ``\verb|$ git ... '@{1 days ago}|''.
-Although such command options are very difficult to remember,
-users can do the same thing only by saying \tt{RE} and \tt{1}.
+A description like ``2日前''(2 days ago) was also shown in the candidate list.
+This means that the user can use the same string ``\tt{git RE 2}''
+for getting the \tt{README.md} file of the day before yesterday.
+The command,
+``\verb|$ git diff '@{2 days ago}' README.md|'',
+is difficult to remember,
+but users can do the same thing only by saying \tt{RE} and \tt{2}.
+
+A Japanese \tt{git} user can do the same thing just like
+English-speaking users.
+
+\begin{figure}[h]
+  % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
+  \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
+  \caption{Invoking {\GH}.}
+  \label{bash2}
+\end{figure}
+
+If the user wants to know more about the command line options,
+he can click the ``i'' button and browse the Wiki page.
+The page can be edited by any user, and
+
+(Figure of Wiki here)
 
@@
 
-{\EH} search algorithm and database structure
+% {\EH} search algorithm and database structure
 
@@
 
-A powerful information retrieval mechanism ``{\EH}'' is used in {\GH}.
+A flexible information retrieval mechanism ``{\EH}'' is used in {\GH}.
 
 Help data used in {\EH} are provided as a set of data entries
-consisting of a regular expression which represents the help entry description
+consisting of a regular expression that represents the help entry description
 and a corresponding command pattern.
@@
 %
-For example, a help entry for finding a restaurant on the Web consists of
-the following data:
+For example, a help entry for showing the difference between
+current file and older file can be like this:
 
@@
   description: \\
-  \stt{Find a (Chinese|Korean|Vietnamese) restaurant \\  in (San Francisco|Chicago|New York) \\  on Yelp.com} \\
+  \stt{Compare (\#{files}) with the one from (1|2|3|4) versions before}\\
   command: \\
-  \stt{open 'http://www.yelp.com/search?\\  find\_loc=\$2\&find\_desc=\$1'}
+  \stt{git diff ....}
 \end{quote}
@@
 is for generating texts like
-\qsf{Find a Chinese restaurant in San Francisco}, 
-\qsf{Find a Chinese restaurant in Chicago}, etc.,
+\qsf{Compare README.md with the one from 1 versions before}, 
+\qsf{Compare index.html with the one from 2 versions before}, etc.,
 and the second part, command part,
-is used to generate a command for accessing \tt{Yelp.com}.
-In the first example, \qsf{Chinese} and \qsf{San Francisco}
+is used to generate a command to execute a \tt{git} command.
+In the first example, \qsf{README.md} and \qsf{1}
 match the first and second parentheses of the regular expression, and
 these values are assigned to \tt{\$1} and \tt{\$2}
-for the command part, generating a URL
-\tt{http://www.yelp.com/search?find\_loc=San\%20Francisco\&find\_desc=Chinese}.
+for the command part, generating a command
+\tt{git xxxxxxx}.
 
-When the matched pattern like \qsf{San Francisco}
-cannot be directly used in the command,
-parameters for the command can be put after the description string,
-separated by a TAB character.
-For example, when a number like ``\tt{29247}'' should be used
-for checking the
-weather of San Francisco, we can describe the help entry like this:
-
-\begin{quote}\small
- description: \\
- \tt{Check the weather of (San Francisco{\textbackslash}t29247| New York{\textbackslash}t23164)} \\
- command: \\
- \tt{open 'http://local.msn.com/ten-day.aspx?\\eid=\$1'}
-\end{quote}
-
-Here, selecting a menu entry \qsf{Check the weather of San Francisco}
-will produce a command
-\tt{open 'http:{\slash}{\slash}local. msn.com{\slash}ten-day.aspx?eid=29247'}.
+% When the matched pattern like \qsf{San Francisco}
+% cannot be directly used in the command,
+% parameters for the command can be put after the description string,
+% separated by a TAB character.
+% For example, when a number like ``\tt{29247}'' should be used
+% for checking the
+% weather of San Francisco, we can describe the help entry like this:
+% 
+% \begin{quote}\small
+%  description: \\
+%  \tt{Check the weather of (San Francisco{\textbackslash}t29247| New York{\textbackslash}t23164)} \\
+%  command: \\
+%  \tt{open 'http://local.msn.com/ten-day.aspx?\\eid=\$1'}
+% \end{quote}
+%
+% Here, selecting a menu entry \qsf{Check the weather of San Francisco}
+% will produce a command
+% \tt{open 'http:{\slash}{\slash}local. msn.com{\slash}ten-day.aspx?eid=29247'}.
 
@@
 
-First, the spec like \verb|#{file}| is expanded to a list of filenames like
+First, the spec like \stt{\#\{file\}} is expanded to a list of filenames like
 \verb+README.md|Makefile|test.c+,
@@
 the spec can be modified to 
-\verb+(delete|remove) a (#{file})+.
+\stt{(delete|remove) a (\#{file})}.
 
@@
 \begin{verbatim}
-  #{file}を(消す|消去する)
+  \#{file}を(消す|消去する)
   /bin/rm $1
@@
 For example, we use a short regular expression
-\qtt{(remove|delete|erase) (data|file)}
+\sqtt{(remove|delete|erase) (data|file)}
 for representing expressions like
-\qsf{remove data},\qsf{erase file}, etc.
+\sqsf{remove data},\sqsf{erase file}, etc.
 
@@
 When we have a regular expression
-\qtt{Find a (Chinese|Korean|Vietnamese) restaurant in (San Francisco|Chicago|New York) on Yelp.com}, 
+\sqtt{Compare (README.md|index.html|package.json) with the one (1|2|...|10) versions before}, 
 we can parse the string and convert it into a state transition diagram
@@
 \begin{figure}[htb]
-\includegraphics[width=90mm,bb=0 0 573 124]{figures/statemachine.pdf}
+\includegraphics[width=90mm,bb=0 0 571 126]{figures/statemachine.pdf}
 \caption{State transition diagram for finding a restaurant.}
@@
 \small
-\textsf{Find a Chinese restaurant in San Francisco} \\
-\textsf{Find a Chinese restaurant in Chicago} \\
+\ssf{Compare README.md with the one 1 versions before} \\
+\ssf{Compare index.html with the one 1 versions before} \\
 ...\\
-\textsf{Find a Vietnamese restaurant in New York}\\
+\ssf{Compare package.json with the one 10 versions beforef}\\
 \end{quote}
@@
 \raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}},
-the system generates a string \qsf{Find a} and proceeds to the next node.
+the system generates a string \sqsf{Compare} and proceeds to the next node.
 In the second generation,
-the system can add \qsf{Chinese}, \qsf{Korean}, and \qsf{Vietnamese}
-to \qsf{Find a}, generating
-\qsf{Find a Chinese}, \qsf{Find a Korean}, etc.
+the system can add \sqsf{README.md}, \sqsf{index.html}, and \sqsf{package.json}
+to \sqsf{Compare}, generating
+\sqsf{Compare README.md}, \sqsf{Compare index.html}, etc.
 The system can repeat finding edges from previously visited nodes,
@@
 Of course, it is impossible to generate all the strings
-from a regular expression like ``\tt{(0|1)+}'' which represents infinite length of
+from a regular expression like ``\tt{(0|1)+}'' that represents infinite length of
 strings consisting of \tt{0}s and \tt{1}s, so the generation should be
@@
 
-``Generate-and-test\footnote{
+``Generate-and-test''\footnote{
   {\sf http:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Generate\_and\_test}
-}''
-technique is a simple and effective strategy
+}
+is a simple and effective strategy
 used for solving puzzles and AI problems.
@@
 This strategy is similar to the
-``Literate Programming'' style,
+``Literate Programming''\footnote{
+  \ssf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Literate\_programming}
+} style,
 where source codes and documents are put in the same document.

### 2018-04-05 paper/paper.tex
...

@@
 % \usepackage[utf8]{inputenc} % for a UTF8 editor only
+
+\usepackage{here} % [H]とするとその場所に配置されるらしい
 
@@
 \begin{figure}[h]
-  % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
-  % \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
-  \includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp1.png}
+  \includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp_e2.png}
   \caption{Invoking {\GH}.}
@@
 descriptios and command strings are listed.
-One of the entries says ``README.mdをふたつ前のバージョンと比較する'',
-which means ``to compare \tt{README.md} with the one from 2 versions before.''
+One of the entries says ``Compare README.md with the one from 2 versions before''.
+% which means ``to compare \tt{README.md} with the one from 2 versions before.''
 %
@@
 
-A description like ``2日前''(2 days ago) was also shown in the candidate list.
+A description like ``2 days ago'' is also shown in the candidate list.
 This means that the user can use the same string ``\tt{git RE 2}''
@@
 The command,
-``\verb|$ git diff '@{2 days ago}' README.md|'',
+``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff '@{2 days ago}' README.md|}'',
 is difficult to remember,
-but users can do the same thing only by saying \tt{RE} and \tt{2}.
-
-A Japanese \tt{git} user can do the same thing just like
+but users can do the same thing only by saying \sqtt{RE} and \sqtt{2}.
+
+A Japanese \stt{git} user can do the same thing just like
 English-speaking users.
 
-\begin{figure}[h]
+\begin{figure}[H]
   % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
@@
 If the user wants to know more about the command line options,
-he can click the ``i'' button and browse the Wiki page.
+he can click the
+\raisebox{-2pt}{\includegraphics[height=11pt,bb=0 0 200 200]{figures/info-xxl.png}}
+button and browse the Wiki page.
 The page can be edited by any user, and
 
-(Figure of Wiki here)
+\begin{figure}[htb]
+\begin{verbatim}
+\end{verbatim}
+% \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
+\centerline{\includegraphics[width=100mm,bb=-50 -50 1000 900]{figures/scrapbox1.png}}
+\caption{A {\SB} page for \tt{git diff}.}
+\label{scrapboxpage}
+\end{figure}
 
@@
 
-% \subsection{Translation}
+\subsection{ExpandHelp}
 
@@
 \begin{quote}
-  description: \\
-  \stt{Compare (\#{files}) with the one from (1|2|3|4) versions before}\\
-  command: \\
-  \stt{git diff ....}
+  \textbf{description}: \\
+  \stt{Compare (\#\{files\}) with the one from (1|2|3|4) versions before}\\
+  \textbf{command}: \\
+  {\fontsize{9pt}{0pt}\selectfont\verb|git diff $(git rev-list -n #{$2} HEAD -- #{$1})^ -- #{$1}|}
 \end{quote}
@@
 is for generating texts like
-\qsf{Compare README.md with the one from 1 versions before}, 
-\qsf{Compare index.html with the one from 2 versions before}, etc.,
+\sqsf{Compare README.md with the one from 1 versions before}, 
+\sqsf{Compare index.html with the one from 2 versions before}, etc.,
 and the second part, command part,
 is used to generate a command to execute a \tt{git} command.
-In the first example, \qsf{README.md} and \qsf{1}
+In the first example, \sqsf{README.md} and \sqsf{1}
 match the first and second parentheses of the regular expression, and
@@
 for the command part, generating a command
-\tt{git xxxxxxx}.
+``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff $(git rev-list -n #{$2} HEAD -- #{$1})^ -- #{$1}|}''.
+
+The description part can be written in any natural language.
+For example,
+
+\begin{quote}
+  \stt{(\#\{files\})を(1|2|3|4)個前のものと比較する}
+\end{quote}
+
+can be used for Japanese users.
+In this case,
+\sqsf{README.mdを1個前のものと比較する},
+\sqsf{README.mdを2個前のものと比較する}, etc.
+are used for theh matching.
 
@@
 
-\subsection{(section written for GitHelp)}
-
-{\EH} is a general-purpose flexible help generation system
-that has the following characteristics.
-
-\begin{itemize}
-\item Use description-execution pairs for the translation
-\item Standard regular expression is used for the specification of the description
-\item The specification RegExp is expanded and filtered by the user's input string
-  real-time
-\end{itemize}
-
-An example of the desc-exec pair can be the following:
-
-\begin{verbatim}
-  (delete|remove) a (#{file})
-  /bin/rm $2
-\end{verbatim}
-
-``remove \verb|README.md|''
-into
-``\verb|rm README.md|
-
-First, the spec like \stt{\#\{file\}} is expanded to a list of filenames like
-\verb+README.md|Makefile|test.c+,
-and the spec string becomes
-``\verb+(delete|remove) a file (README.md|Makefile|test.c)+''.
-Then this regular expression is expanded to all the possible string that match this regexp like
-\begin{verbatim}
-delete a file README.md
-remove a file README.md
-delete a file Makefile
-remove a file Makefile
-...
-\end{verbatim}
-
-And then all these strings are compared with the user's specification like
-``\verb|del REA|'',
-and if a matche is found,
-this is translated to
-``\verb|delete file README.md|''.
-
-If ``\verb|destroy|'' should also be used for the spec,
-the spec can be modified to 
-\stt{(delete|remove) a (\#{file})}.
-
-Any kind of specs in any language can be used for the specification.
-For example,
-
-\begin{verbatim}
-  \#{file}を(消す|消去する)
-  /bin/rm $1
-\end{verbatim}
-
-can be  used for Japanese users, who might want to delete
-one of the files by specifying ``消す''.
-(消す means 'delete' in Japanese).
-
-\subsection{Generating help menu entries}
+%% \subsection{(section written for GitHelp)}
+%% 
+%% {\EH} is a general-purpose flexible help generation system
+%% that has the following characteristics.
+%% 
+%% \begin{itemize}
+%% \item Use description-execution pairs for the translation
+%% \item Standard regular expression is used for the specification of the description
+%% \item The specification RegExp is expanded and filtered by the user's input string
+%%   real-time
+%% \end{itemize}
+%% 
+%% An example of the desc-exec pair can be the following:
+%% 
+%% \begin{verbatim}
+%%   (delete|remove) a (#{file})
+%%   /bin/rm $2
+%% \end{verbatim}
+%% 
+%% ``remove \verb|README.md|''
+%% into
+%% ``\verb|rm README.md|
+%% 
+%% First, the spec like \stt{\#\{file\}} is expanded to a list of filenames like
+%% \verb+README.md|Makefile|test.c+,
+%% and the spec string becomes
+%% ``\verb+(delete|remove) a file (README.md|Makefile|test.c)+''.
+%% Then this regular expression is expanded to all the possible string that match this regexp like
+%% \begin{verbatim}
+%% delete a file README.md
+%% remove a file README.md
+%% delete a file Makefile
+%% remove a file Makefile
+%% ...
+%% \end{verbatim}
+%% 
+%% And then all these strings are compared with the user's specification like
+%% ``\verb|del REA|'',
+%% and if a matche is found,
+%% this is translated to
+%% ``\verb|delete file README.md|''.
+%% 
+%% If ``\verb|destroy|'' should also be used for the spec,
+%% the spec can be modified to 
+%% \stt{(delete|remove) a (\#{file})}.
+%% 
+%% Any kind of specs in any language can be used for the specification.
+%% For example,
+%% 
+%% \begin{verbatim}
+%%   \#{file}を(消す|消去する)
+%%   /bin/rm $1
+%% \end{verbatim}
+%% 
+%% can be  used for Japanese users, who might want to delete
+%% one of the files by specifying ``消す''.
+%% (消す means 'delete' in Japanese).
+
+\subsubsection{Generating help menu entries}
 
@@
 
-\subsubsection{Phase 1: Generating a state transition diagram from a regular expression}
+\paragraph{Phase 1: Generating a state transition diagram from a regular expression}
 
@@
 
-\subsubsection{Phase 2: Generating texts from a state transition diagram}
+\paragraph{Phase 2: Generating texts from a state transition diagram}
 
@@
 
-\subsection{Generate-and-Filter}
+\subsubsection{Generate-and-Filter}
 
@@
 
-\subsection{Approximate pattern matching by shifter algorithm}
-
-簡潔に書けるか?
-
-\subsection{Sharing database on the Web}
+\subsubsection{Approximate pattern matching by shifter algorithm}
+
+The ``shifter algorithm''\cite{Wu:1992:FTS:135239.135244}
+is a simple and efficient
+text search algorithm which has interesting features
+not found in more common pattern matching algorithms like
+KMP\cite{KMP}, Boyer-Moor\cite{Boyer:1977:FSS:359842.359859}, etc.
+
+When a user wants to find a word \qsf{README} in a text,
+he can use a patter matching state machine like below,
+where the gray circle denotes that the state is active.
+
+\begin{figure}[h]
+\includegraphics[width=70mm,bb=0 0 439 73]{figures/readme1.pdf}
+\caption{A state machine for \qsf{README}.}
+\label{readme1}
+\end{figure}
+
+Initially, only the leftmost node is active, but when the
+state machine receives \qsf{R}, both the first and the second node become active
+and the activation state will change to the following pattern.
+
+\begin{figure}[h]
+\includegraphics[width=70mm,bb=0 0 439 73]{figures/readme2.pdf}
+\caption{After receiving \qsf{R}.}
+\label{readme2}
+\end{figure}
+
+When \qsf{README} is given to the state machine,
+the rightmost node becomes active.
+
+\begin{figure}[h]
+\includegraphics[width=70mm,bb=0 0 439 73]{figures/readme3.pdf}
+\caption{After receiving \qsf{README}.}
+\label{readme3}
+\end{figure}
+
+Although this state machine is a nondeterministic finite automata (NFA),
+only 10 bits are required to represent the active/inactive states of the nodes,
+meaning that the whole states can be represented by a single integer value.
+Also,
+the state transition can be calculated by a simple combination of
+logic and bit shift operations.
+
+%% We will describe how the pattern matching can be performed using a C code.
+%% 
+%% First, a variable for current state is
+%% set to \stt{0x80000000}, representing the initial pattern
+%% shown in Figure \ref{readme1}.
+%% 
+%% {
+%% \scriptsize
+%% \begin{verbatim}
+%%  #define INITPAT 0x80000000
+%%  int state = INITPAT;
+%% \end{verbatim}
+%% }
+%% 
+%% When character \qsf{r} is received, the MSB will be shifted to the right
+%% by one bit, and logical OR is calculated with the initial value, \stt{0x80000000}.
+%% Since the 7th node also accepts \qsf{r}, it should also be shifted.
+%% The state transition can be described like below.
+%% 
+%% {
+%% \scriptsize
+%% \begin{verbatim}
+%%  mask['r'] = 0x82;
+%%  state = INITPAT | ((state & mask['r']) >> 1);
+%% \end{verbatim}
+%% }
+%% 
+%% The shift ``mask'' value can be easily calculated from the given
+%% pattern string beforehand.
+%% 
+%% {
+%% \scriptsize
+%% \begin{verbatim}
+%%   int maskpat;
+%%   init(pat){
+%%     maskpat= INITPAT;
+%%     for(char *s=pat;*s;s++){
+%%       mask[*s] |= maskpat;
+%%       maskpat >>= 1;
+%%     }
+%%     acceptpat = maskpat;
+%%   }
+%% \end{verbatim}
+%% }
+%% 
+%% The pattern matching function can be described like below.
+%% 
+%% {
+%% \scriptsize
+%% \begin{verbatim}
+%%  match(s){
+%%    int state = INITPAT;
+%%    for(s=text;*s;s++){
+%%      state = INITPAT | ((state & mask[*s]) >> 1);
+%%    }
+%%    return ((state & acceptpat) != 0);
+%%  }
+%% \end{verbatim}
+%% }
+
+\subsubsection{Approximate pattern matching using the shifter algorithm}
+
+The state machine shown in Figure \ref{readme1} can accept only one pattern
+(\sqsf{README}), but
+it can be easily expanded to detect texts which contain a word
+similar to the pattern (e.g. \sqsf{READY}).
+
+%   *  ** 
+%  risto rante
+%  restaurant
+\begin{figure}[htb]
+\begin{verbatim}
+\end{verbatim}
+\centerline{\includegraphics[width=40mm,bb=0 0 104 51]{figures/readme-mismatch.pdf}}
+\caption{Matching error between \qsf{README} and \qsf{REDDY}.}
+\label{readme-reddy-mismatch}
+\end{figure}
+
+Adding three more states to Figure \ref{readme1}, we can perform more
+sophisticated pattern matcher which can accept strings with
+0 to 3 matching errors.
+
+\begin{figure}[htb]
+\includegraphics[width=85mm,bb=0 0 443 282]{figures/readme-ambig.pdf}
+\caption{A pattern matcher accepting 0-3 errors.}
+\label{shifterambig}
+\end{figure}
+
+Figure \ref{shifterambig} shows a state machine which can detect a string
+which matches \sqsf{README} with 0 to 3 mismatches.
+Each additional row of nodes represents a matcher with one error,
+two errors, and three errors, respectively.
+Vertical and diagonal transition edges are added to allow
+transitions based on spelling errors.
+
+Initially, only the bottom-left node is active.
+When a character other than \sqsf{R} is detected, 
+the transition labeled \sqsf{*} (wildcard) is activated,
+and connected nodes become active.
+At the same time, links labeled as ``$\epsilon$''
+is also activated without any input character.
+With these additional links, this expanded machine can detect a text which
+matches \sqsf{README} with 0 to 3 errors.
+
+% \begin{figure}[htb]
+% \includegraphics[width=82mm]{figures/restaurant-ristrante.pdf}
+% \caption{Accepting ``\tsf{ristorante}'' using a matcher for ``\tsf{restaurant}''.}
+% \label{restaurant-ristorante}
+% \end{figure}
+
+The transition of active nodes while reading
+\sqsf{REDDY} is shown in Figure \ref{restaurant-ristorante}.
+After reading \sqsf{REDDY},
+only the upper-right node becomes active,
+denoting that \sqsf{REDDY} matches
+\sqsf{README}'' with 3 matching errors.
+
+The state transition shown in 
+Figure \ref{restaurant-ristorante} looks complicated, but
+the matching state can be represented by only four integer variables, and
+the matching algorithm is not very different from the algorithm
+shown above.
+
+\subsubsection{Using the matcher for generate-and-filter}
+
+We can use this approximate pattern matcher while generating
+help texts by traversing the state transition machine.
+%
+Every time a new node is generated by traversing an edge,
+matching state is calculated and stored in the generated node.
+The status pattern is calculated from the status pattern
+stored in the preceding node and the string associated with the edge.
+
+% \begin{figure}[htb]
+% \includegraphics[width=85mm]{figures/ristfrans1.pdf}
+% \caption{A pattern matcher for ``\ttt{rist frans}''.}
+% \label{ristfrans1}
+% \end{figure}
+% 
+% \begin{figure*}[bht]
+% \centerline{\includegraphics[width=110mm]{figures/gentree2.pdf}}
+% \caption{Matching statuses for ``\ttt{rist frans}'' associated with text generation nodes.}
+% \label{gentree2}
+% \end{figure*}
+
+% Figure \ref{ristfrans1} shows the matcher for \qtt{rist frans}\footnote{
+%   A space (\qtt{ }) in the input is treated as a wildcard character.
+% },
+% and Figure \ref{gentree2} shows how the matching status is calculated while the
+% description strings are generated from the state transition machine
+% shown in Figure \ref{statemachine1}.
+% The matching status at each node is calculated from the matching status
+% stored in the parent node and the string associated with the edge.
+% For example, when the system generates the string
+% \qsf{Find a Chinese restaurant in San Francisco on Yelp.com},
+% the matching status is calculated from the status data at the previous node at
+% \qsf{Find a Chinese restaurant in San Francisco}, and
+% the system can tell that it matches \qtt{rist frans} with two matching errors,
+% as soon as the string is generated.
+
+% The system is keeping the list of generated strings
+% which match the pattern with zero to three errors
+% and it displays the list with minimal number of errors
+% when generating menu entries.
+% 
+% Since the pattern matching operation is performed at the time of text generation,
+% the whole generate-and-filter calculation is quick.
+% Although current version of ExpandHelp is implemented in MacRuby,
+% the user can always get the result within 1 second.
+% A portion of the help data in Ruby is shown in Figure \ref{helpdata}.
+
+% \begin{figure*}[bt]
+% \centerline{\includegraphics[width=146mm]{figures/04ad7dee5679450e5390821745b5a0b7.png}}
+% \caption{A portion of the help data in Ruby.}
+% \label{helpdata}
+% \end{figure*}
+
+\subsection{Sharing the database on the Web}
 
@@
 on Web browsers just like text editors,
-using simple markup symbols similar to MarkDown\footnote{markdown}
-and other markup languages.
-
-For {\GH}, database entries like the following
+using simple markup symbols.
+
+The data used for {\GH} is shown in Figure \ref{scrapboxpage}.
 
@@
 % \end{verbatim}
-% \centerline{\includegraphics[width=40mm]{figures/xxxxx}}
-% \caption{ssss}
+% % \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
+% \centerline{\includegraphics[width=100mm,bb=-50 -50 1000 900]{figures/scrapbox1.png}}
+% \caption{A {\SB} page for \tt{git diff}.}
 % \label{xxxxx}
@@
 
-This page describes the usage of \qtt{git diff}, and
+This page describes the usage of \sqtt{git diff}, and
 the page contains command specifications in {\EH} format
-in addition to the description of the command.
+in addition to the description of \sqtt{git diff}.
 %
@@
 %
-When a user types the TAB key after typing \qtt{la} on the Unix shell,
-\qtt{latex}, \qtt{latex}, and other commands are shown as candidates.
-When a user types \qtt{ls RE} and types the TAB key,
-Unix shell checks the directory, find the \tt{README.md} file, and
-replace the user's input with \qtt{ls README.md}.
+When a user types the TAB key after typing \sqtt{la} on the Unix shell,
+\sqtt{latex}, \sqtt{latex}, and other commands are shown as candidates.
+When a user types \sqtt{ls RE} and types the TAB key,
+Unix shell checks the directory, find the \stt{README.md} file, and
+replace the user's input with \sqtt{ls README.md}.
 This behavior is called ``text completion'', and many variations of
@@
 For example,
-\qtt{ActiveDocument .PageSetup .LeftMargin = InchesToPoints(2)}
+\sqtt{ActiveDocument .PageSetup .LeftMargin = InchesToPoints(2)}
 can be generated from keywords like
-\qsf{left},
-\qsf{margin},
-\qsf{4}, and
-\qsf{inches}.
+\sqsf{left},
+\sqsf{margin},
+\sqsf{4}, and
+\sqsf{inches}.
 The system generates the code using a template database and heuristics
@@
 can generate a code snippet from abbreviation strings give by the user.
-For example, a snippet like \qtt{chooser. showOpenDialog()}
+For example, a snippet like \sqtt{chooser. showOpenDialog()}
 can be generated from the keyword
-\qsf{ch} and\qsf{opn}, using the code database and HMM.
+\sqsf{ch} and\sqsf{opn}, using the code database and HMM.
 It can be very useful as a shorthand for handling long names,
 but users should have a vague knowledge about the correct names
-(e.g. \qtt{chooser}, \qtt{dialog}),
+(e.g. \sqtt{chooser}, \sqtt{dialog}),
 and large code example corpus should exist before

### 2018-04-05 app/githelp.js

@@ -6,7 +6,8 @@ const remote = electron.remote;
 const shell = electron.shell;
 const clipboard = electron.clipboard; // clipboard.writeText() でクリップボードに文字列が入る
 
-const data = require("./data");
+// const data = require("./data");
+const data = require("./data_e");
 Generator = require('re_expand');
 
 ///var command = 'osascript -e \'tell application "Terminal" to tell front window to set the clipboard to contents of selected tab as text\' ';

### 2018-04-05 paper/paper.tex
...

@@
 ``\verb|HEAD^^|''
-for specifying an old version.
+for specifying the old version.
 
@@
 
-Nothing happens here because
+However, nothing happens here because
 \verb|HEAD^^|
 specifies a file included in the older commit,
-and the command above only compares the \tt{README.md}
+and the command above only compares the \stt{README.md}
 with the file included in an old commit, where
-\tt{README.md} might be the same as the latest version.
+\stt{README.md} might be the same as the latest version.
 
@@
 % (e.g. \tt{Cmd-Ctrl-G})
-to invoke {\GH} after typing ``\verb|git RE 2|'' to see how he can do the job.
+to invoke {\GH} after typing \stt{git RE 2} to see how he can
+perform the task.
 
@@
   \includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp_e2.png}
-  \caption{Invoking {\GH}.}
+  \caption{Invoking {\GH} after typing \stt{git rea 2}.}
   \label{bash1}
@@
 descriptios and command strings are listed.
-One of the entries says ``Compare README.md with the one from 2 versions before''.
-% which means ``to compare \tt{README.md} with the one from 2 versions before.''
-%
+One of the entries says
+``\ssf{Compare} \stt{README.md} \ssf{with the one from 2 versions before}''.
 If the user thinks that that's what he wants to do,
-he can select the entry by selecting it by typing arrow keys
-and type the enter key.
+he can select the entry by typing arrow keys and type the enter key.
 Then the user's input string is replaced by the right command string
@@
 A description like ``2 days ago'' is also shown in the candidate list.
-This means that the user can use the same string ``\tt{git RE 2}''
-for getting the \tt{README.md} file of the day before yesterday.
+This means that the user can use the same string \sqtt{git RE 2}
+for getting the \stt{README.md} file of the day before yesterday.
 The command,
 ``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff '@{2 days ago}' README.md|}'',
-is difficult to remember,
-but users can do the same thing only by saying \sqtt{RE} and \sqtt{2}.
+may not be familiar to most \tt{git} users,
+but users can perform this task only by giving \sqtt{RE} and \sqtt{2}.
 
@@
 English-speaking users.
+He can user the term \qtt{比}(compare) to find how he can perfor the job.
 
@@
 
-If the user wants to know more about the command line options,
+If the user wants to know more about the command line,
 he can click the
 \raisebox{-2pt}{\includegraphics[height=11pt,bb=0 0 200 200]{figures/info-xxl.png}}
-button and browse the Wiki page.
-The page can be edited by any user, and
+button and see the Wiki page shown in Figure \ref{scrapboxpage}.
+The user can edit the page if he wants to add information or finds an error.
 

### 2018-04-05 paper/paper.tex
...

@@
 
+% 4/5 17:00 PDT = 4/6 9:00 JST
+
 % 部屋を暗くする
 % make the room darker
-% iot ......
 
@@
 \def\EH{\textsf{ExpandHelp}}
+\def\GIT{\texttt{git}}
 \long\def\tt#1{\texttt{#1}}
@@
   in the {\GH} system
-  with which user can easily generate complex \tt{git} commands
+  with which user can easily generate complex {\GIT} commands
   from fragments of users' intentions.
@@
 with which a user can translate his vague intention in various languages
-into a complete \tt{git} command
+into a complete {\GIT} command
 using the {\EH} framework.
@@
 with the same file from 2 versions before,
-he might try to use \tt{git} with an argument
+he might try to use {\GIT} with an argument
 ``\verb|HEAD^^|''
@@
 
-A description like ``2 days ago'' is also shown in the candidate list.
+A description like \sqsf{2 days ago} is also shown in the candidate list.
 This means that the user can use the same string \sqtt{git RE 2}
@@
 ``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff '@{2 days ago}' README.md|}'',
-may not be familiar to most \tt{git} users,
+may not be familiar to most {\GIT} users,
 but users can perform this task only by giving \sqtt{RE} and \sqtt{2}.
 
-A Japanese \stt{git} user can do the same thing just like
+A Japanese {\GIT} user can do the same thing just like
 English-speaking users.
@@
 
-\begin{figure}[H]
+\begin{figure}[t]
   % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
@@
 
-\begin{figure}[htb]
+\begin{figure}[b]
 \begin{verbatim}
@@
 
-% {\EH} search algorithm and database structure
-
 \subsection{ExpandHelp}
@@
 A flexible information retrieval mechanism ``{\EH}'' is used in {\GH}.
-
+%
 Help data used in {\EH} are provided as a set of data entries
 consisting of a regular expression that represents the help entry description
-and a corresponding command pattern.
+and a corresponding command pattern string.
 A description string is used to produce natural language texts
 that are easily understandable by users,
-while command patterns are used for invoking commands or calling library functions
+while command patterns are used for invoking commands
 corresponding to the description.
@@
 and the second part, command part,
-is used to generate a command to execute a \tt{git} command.
+is used to generate a command to execute a {\GIT} command.
 In the first example, \sqsf{README.md} and \sqsf{1}
@@
 \sqsf{README.mdを2個前のものと比較する}, etc.
-are used for theh matching.
+are used for the matching.
 
@@
 Finding appropriate entries from the huge help document space is performed in two steps.
-First, we parse the regular expression to
-generate a state transition diagram that represents all the strings represented
-in the regular expression.
-Second, we generate all the description strings by expanding the regular expression
+First, a state transition diagram is generated from the regular expressions
+used in the descriptions.
+Second, all the description strings are generated by expanding the regular expression
 into a tree, and filter the generated strings by the pattern specified by the user.
@@
 is a simple and efficient
-text search algorithm which has interesting features
+text search algorithm that has interesting features
 not found in more common pattern matching algorithms like
@@
 
-When a user wants to find a word \qsf{README} in a text,
+When a user wants to find a word \sqsf{README} in a text,
 he can use a patter matching state machine like below,
@@
 \begin{figure}[h]
-\includegraphics[width=70mm,bb=0 0 439 73]{figures/readme1.pdf}
+  \includegraphics[width=60mm,bb=0 0 439 73]{figures/readme1.pdf}
   \caption{A state machine for \qsf{README}.}
@@
 \begin{figure}[h]
-\includegraphics[width=70mm,bb=0 0 439 73]{figures/readme2.pdf}
+\includegraphics[width=60mm,bb=0 0 439 73]{figures/readme2.pdf}
 \caption{After receiving \qsf{R}.}
@@
 \begin{figure}[h]
-\includegraphics[width=70mm,bb=0 0 439 73]{figures/readme3.pdf}
+\includegraphics[width=60mm,bb=0 0 439 73]{figures/readme3.pdf}
 \caption{After receiving \qsf{README}.}
@@
 \begin{figure}[htb]
-\begin{verbatim}
-\end{verbatim}
   \centerline{\includegraphics[width=40mm,bb=0 0 104 51]{figures/readme-mismatch.pdf}}
@@
 Adding three more states to Figure \ref{readme1}, we can perform more
-sophisticated pattern matcher which can accept strings with
+flexible pattern matcher which can accept strings with
 0 to 3 matching errors.
@@
 \begin{figure}[htb]
-\includegraphics[width=85mm,bb=0 0 443 282]{figures/readme-ambig.pdf}
+  \includegraphics[width=65mm,bb=0 0 443 282]{figures/readme-ambig.pdf}
   \caption{A pattern matcher accepting 0-3 errors.}
@@
 {\SB} users can edit the contents of Wiki pages directly
-on Web browsers just like text editors,
-using simple markup symbols.
+on Web browsers just like using text editors.
 
@@
 
-This page describes the usage of \sqtt{git diff}, and
+This page shows how to use \sqtt{git diff}, and
 the page contains command specifications in {\EH} format
-in addition to the description of \sqtt{git diff}.
-%
+in addition to the documentation.
+
 % Specs and command lines are specified with a special symbol, and
@@
 
-Although usage examples are often shown on Unix man pages,
-they cannot be used as the database of online help system.
+Usage examples are often shown on documents and manuals like Unix man pages,
+they cannot be used as the database of an online help system.
 On the other hand,
-a {\SB} document contains both the manual page and the help database
-at the same place.
-%
-This strategy is similar to the
-``Literate Programming''\footnote{
+a {\SB} document contains both the manual document and the help database
+in the same place, just like
+writing a source code and the document in the same place
+using the ``Literate Programming''\footnote{
   \ssf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Literate\_programming}
-} style,
-where source codes and documents are put in the same document.
+} style.
 
@@
 use translation systems for using computers.
-Using an additional translation system like {\GH} is ...
+
+The behavior of {\GH} is similar to conventional IMs.
 
@@
 When a user types the TAB key after typing \sqtt{la} on the Unix shell,
-\sqtt{latex}, \sqtt{latex}, and other commands are shown as candidates.
+\sqtt{latex}, \sqtt{latex}, and other Unix commands are shown as candidates.
 When a user types \sqtt{ls RE} and types the TAB key,
-Unix shell checks the directory, find the \stt{README.md} file, and
+the shell checks the directory, find the \stt{README.md} file, and
 replace the user's input with \sqtt{ls README.md}.
 This behavior is called ``text completion'', and many variations of
-this idea have been proposed and adopted in text editors and command line editors.
+this idea have been proposed and adopted in command shells and text editors.
 
@@
 
-% Programing-by-Example (PBE) systems\cite{Cypher}\cite{Lieberman}.
-
 Gitsome\footnote{\textsf{https:{\slash}{\slash}github.com{\slash}donnemartin{\slash}gitsome}}
-helps \tt{git} users by
+helps {\GIT} users by
 dynamically showing possible arguments and related manuals on the Unix shell,
@@
 
-Many smart IDEs for suggesting codes have been proposed resently.
-
-% 賢い補完
+Integrated Development Environments (IDEs) are widely used for
+software development, and
+many smart IDEs for suggesting codes have been proposed resently.
+
 Little's system\cite{Little:2006:TKC:1166253.1166275}
-generates a complete JavaScript code snippet from keyword fragments.
-For example,
+generates a complete JavaScript code snippet from keyword fragments
+give by users.
+For example, a code snippet
 \sqtt{ActiveDocument .PageSetup .LeftMargin = InchesToPoints(2)}
@@
 \sqsf{margin},
-\sqsf{4}, and
-\sqsf{inches}.
+\sqsf{inches},
+and \sqsf{2}.
 The system generates the code using a template database and heuristics
-for the target system.
-It is useful for a special environment, but
+designed for the target system.
+It is useful for a specific environment, but
 users of the system cannot modify the algorithm or the database
@@
 can generate a code snippet from abbreviation strings give by the user.
-For example, a snippet like \sqtt{chooser. showOpenDialog()}
-can be generated from the keyword
-\sqsf{ch} and\sqsf{opn}, using the code database and HMM.
+For example, a code snippet like \sqtt{chooser. showOpenDialog()}
+can be generated from strings like
+\sqsf{ch} and \sqsf{opn}, using the code database and HMM.
 It can be very useful as a shorthand for handling long names,
@@
 
-\section{Evaluation}
+\section{Discussions}
+
+Since the translation mechanism of {\EH} is simple and flexible,
+it can be used for a wide range of application domains where
+intelligent help is required.
+{\EH} can be used for
+
+\paragraph{Order of command and arguments}
+
+Using a command shell,
+users have to enter a command first and enter options and arguments after that.
+Using a GUI desktop,
+users can right-click a data icon to show a menu,
+and select what he wants to do from the menu.
+Switching between command-oriented usage pattern and
+data-oriented usage pattern is sometimes confusing.
+Using {\EH}, users can find what they can do
+either by specifying commands or by specifying data, 
+without worrying about the order.
+
+\paragraph{Usage of regular expressions}
+
+An advantage of using a regular expression is that
+it is fairly easy for users to write description texts.
+People can easily write a help description like
+\sqtt{(Start|Run) Firefox browser}
+without having a knowledge of automata or formal grammar.
+We can use arbitrary texts for the database of Expand Help.
+For example,
+we can collect hundreds of books titled ``Windows tips'' from the market
+and convert all the title of the tips into help data of ExpandHelp.
+
+\paragraph{Toward more general help system}
+
+Since a user can activate a command or access a Web page
+from ExpandHelp only by typing keywords,
+it can be used as a command launcher rather than a help system.
+Adding data to an existing help system is usually a hard task,
+but adding data so ExpandHelp is very simple.
+It would also be convenient to use a Wiki page for providing the help
+data for ExpandHelp, since users can easily edit the description
+for their needs.
+We are planning to distribute Wiki-based ExpandHelp to the public and
+share the help data between groups of people.
 
@@
 
-% REFERENCES FORMAT
+We have introduced a general-purpose flexible translation framework {\EH}
+and used it for {\GH}, a system for supporting {\GIT} users.
+%
+The database of {\EH} are shared on a real-time general-purpose Wiki system {\SB},
+and all the users can share it to improve the quality of the help system.
+
+Unlike existing smart IDEs for supporting programming tasks,
+{\EH} framework can be used in wide range of situations
+where translation-based help is required.
+
+We presented a powerful and flexible help system ``ExpandHelp''
+constructed on the generate-and-filter algorithm, where
+the system generates all the possible expressions of
+help entries expanded from regular expressions given by the help data provider,
+while the output expressions are filtered by search keywords using
+an efficient approximate pattern matching algorithm.
+Since the data format is simple and the search algorithm is fast and flexible,
+developers can easily publish useful help data, while
+users can have bigger chances of finding an appropriate
+data from vague knowledges.
+
 % References must be the same font size as other body text.
+% そうなん?
 \bibliographystyle{SIGCHI-Reference-Format}

### 2018-04-05 paper/paper.tex
...

@@
 %Conference
-\conferenceinfo{UIST'18,}{May 07--12, 2016, San Jose, CA, USA}
+\conferenceinfo{UIST'18,}{October 14--17, 2018, Berlin, Germany}
 %Price
@@
 \def\plaintitle{Bridging the Translation Gap with ExpandHelp}
-\def\plainauthor{First Author, Second Author, Third Author,
-  Fourth Author, Fifth Author, Sixth Author}
+\def\plainauthor{Toshiyuki Masui, Jun Kato}
 \def\emptyauthor{}
-\def\plainkeywords{Authors' choice; of terms; separated; by
-  semicolons; include commas, within terms only; required.}
-\def\plaingeneralterms{Documentation, Standardization}
+\def\plainkeywords{
+  Help systems; Regular expression, Input method, Generate and filter;
+  ExpandHelp; GitHelp
+}
+% \def\plaingeneralterms{Documentation, Standardization}
 
@@
 \long\def\qit#1{``\textit{#1}''}
+\long\def\smallfont{\fontsize{9pt}{0pt}\selectfont}
 
@@
 \author{%
-  \alignauthor{Toshiyuki Masui
+  \alignauthor{Toshiyuki Masui \\
     \affaddr{Keio University}\\
@@
 \begin{abstract}
-  We introduce a flexible command translation system that can generate
+  We introduce a flexible command translation framework that can generate
   a complex command string from vague keywords
@@
   there is usually a huge mismatch between the users' intention
-  and the required action.
+  and required actions.
   % the language and vocabularies used for the task are completely different.
@@
   Translation gaps exist even for experienced computer users, but
-  they are serious for vast amount of people around the world.
-  %
-  We propose a simple and general translation framework
+  they are serious for vast amount of people
+  whose mother languages are far from the command syntax required for
+  handling computers.
+  %
+  We propose a simple and flexible translation framework
   {\EH} that can be used in various situations
-  where such translation is required.
+  where such translation is necessary.
   We show how our framework can be used
@@
   with which user can easily generate complex {\GIT} commands
-  from fragments of users' intentions.
+  from fragments of users' intentions in various languages.
 \end{abstract}
@@
 \category{H.5.m.}{Information Interfaces and Presentation
-  (e.g. HCI)}{Miscellaneous} \category{See
-  \url{http://acm.org/about/class/1998/} for the full list of ACM
-  classifiers. This section is required.}{}{}
+  (e.g. HCI)}{Miscellaneous}
+
+% \category{See
+%   \url{http://acm.org/about/class/1998/} for the full list of ACM
+%   classifiers. This section is required.}{}{}
 
@@
 %
-Even when manuals and help systems are provided,
+Even when manuals and help documents are provided,
 people don't use them\cite{Novick:2006:WDP:1166324.1166329}
@@
 turn the faucet on to fill the glass with water.
-All the living creatures are performing such translations
+In either of these cases, there is a tremendous gap
+betwee the user's intentions and required actions.
+All the living creatures are seemingly performing such translations
 between intentions and actions without difficulty, but
@@
 
-Even when people vaguely know what they have to do for what they want to do,
-it is often not easy for them to perform the task properly.
+Even when people almost know what they have to do,
+it is often not easy for them to perform the task without confusion.
 Even when people know that they can watch a movie on the Internet,
 finding a movie and playing it is a difficult task for people without experiences.
-It would be nicer if they could watch a movie on the net
-just by showing a vague title or attributes of the movie
-in various languages.
+It would be nicer if they could watch a movie
+just by showing a fragment of the title or attributes of the movie.
 
@@
 We propose a simple, flexible and powerful
-translation framework with which users can generate a complete
+translation framework {\EH}, with which users can generate a complete
 command string from fragments of users' vague intentions.
 %
-We provide a database consisting of pairs of
+We use a database consisting of pairs of
 the description of the task that users want to perform (e.g. 房間暗一点)
@@
 Descriptions can be written in any natural language using regular expressions
-and the database on the Wiki pages can be edited by any user
+and the database are shared on the Wiki pages and can be edited by any user
 who wants to improve the database.
@@
 \item Introduction of ``\textit{translation paradigm}'' for
-  generating a correct instruction to an artifact from
-  the user's vague intention in natural language.
-\item General-purpose flexible dynamic search system based on regular expressions.
+  generating a correct command to an artifact from
+  the user's vague intention.
+\item Flexible dynamic help extraction algorithm
+  ``\textit{generate and filter}''
+  using regular expressions.
 % そのための柔軟なインフラ (ExpandHelp)
@@
 % やりたいことを実行するインタフェース (IME的なもの)
-\item Data sharing infrastructure for the above strategy.
+\item Help data sharing infrastructure for the above strategy.
 % 共有/編集しやすい正規表現DSLとそのインプリ(Scrapbox+)
@@
 
-\subsection{Entering a command}
+% \subsection{Entering a command}
 
@@
 development activities.
-
-% \begin{figure}[h]
-%   \includegraphics[width=8cm,bb=0 0 670 254]{figures/bash1.png}
-%   \caption{Bash shell.}
-%   \label{bash1}
-% \end{figure}
-
-When a user wants to compare the latest \tt{README.md} file
+% 
+When a user wants to compare the latest \stt{README.md} file
 with the same file from 2 versions before,
-he might try to use {\GIT} with an argument
-``\verb|HEAD^^|''
+he might try to use {\GIT} with an option
+``{\smallfont\verb|HEAD^^|}''
 for specifying the old version.
 
-\begin{quotation}
+\begin{figure}[h]
+  {\smallfont
   \verb|$ git diff HEAD^^ README.md|
@@
   \verb|$|
-\end{quotation}
+  }
+  \caption{Invoking \stt{git diff}.}
+  \label{gitdiff}
+\end{figure}
+
+% \begin{quotation}
+%   {\smallfont
+%   \verb|$ git diff HEAD^^ README.md|
+%   \par
+%   \verb|$|
+%   }
+% \end{quotation}
 
@@
 specifies a file included in the older commit,
-and the command above only compares the \stt{README.md}
-with the file included in an old commit, where
-\stt{README.md} might be the same as the latest version.
+and the command in figure \ref{gitdiff} only compares the
+\stt{README.md} with the file included in an old commit, where
+\stt{README.md} has not been changed since then.
 
@@
 % (e.g. \tt{Cmd-Ctrl-G})
-to invoke {\GH} after typing \stt{git RE 2} to see how he can
+to invoke {\GH} after typing \sqtt{git RE 2} to see how he can
 perform the task.
@@
 \begin{figure}[h]
-  \includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp_e2.png}
-  \caption{Invoking {\GH} after typing \stt{git rea 2}.}
-  \label{bash1}
+  % \includegraphics[width=9cm,bb=0 0 1194 822]{figures/example1.png}
+  \includegraphics[width=9cm,bb=0 0 900 600]{figures/example1.png}
+  %\includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp_e2.png}
+  \caption{Invoking {\GH} after typing \stt{git read 2}.}
+  \label{example1}
 \end{figure}
@@
 Here, various candidate entries with
-descriptios and command strings are listed.
+descriptions and command strings are listed,
+just like text input support systems for non-English languages.
 One of the entries says
-``\ssf{Compare} \stt{README.md} \ssf{with the one from 2 versions before}''.
-If the user thinks that that's what he wants to do,
+``\ssf{Compare} \stt{README.md} \ssf{with the one from 2 versions before}'',
+and if the user thinks that's what he wants to do,
 he can select the entry by typing arrow keys and type the enter key.
@@
 
-A description like \sqsf{2 days ago} is also shown in the candidate list.
+A description like \sqsf{2 days ago} is also shown in the candidate list
+of Figure \ref{example1}.
 This means that the user can use the same string \sqtt{git RE 2}
-for getting the \stt{README.md} file of the day before yesterday.
-The command,
-``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff '@{2 days ago}' README.md|}'',
+for getting the information of \stt{README.md} file of the day before yesterday.
+The generated argument
+``{\smallfont\verb|@{2 days ago}|}'',
 may not be familiar to most {\GIT} users,
-but users can perform this task only by giving \sqtt{RE} and \sqtt{2}.
+but users can perform this task only by giving \sqtt{RE} and \sqtt{2}
+without knowing the correct syntax of this option.
+
+When the user types a special shortcut key
+after typing \sqtt{git sh reed 3},
+entries related to \stt{README.md} file are listed because
+\sqtt{reed} is close to \sqtt{README.md}.
+
+\begin{figure}[h]
+  %\includegraphics[width=9cm,bb=0 0 1100 760]{figures/example2.png}
+  \includegraphics[width=9cm,bb=-100 0 800 550]{figures/example2.png}
+  \caption{Invoking {\GH} after typing \stt{git sh reed 3}.}
+  \label{example2}
+\end{figure}
 
 A Japanese {\GIT} user can do the same thing just like
-English-speaking users.
-He can user the term \qtt{比}(compare) to find how he can perfor the job.
+English-speaking users (Figure \ref{example3}).
+He can user the term \qtt{比}, etc. to find how he can perform the job.
 
 \begin{figure}[t]
-  % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
+  % bb=0 0 1290 866
   \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
-  \caption{Invoking {\GH}.}
-  \label{bash2}
+  \caption{Invoking {\GH} in Japanese environment.}
+  \label{example3}
 \end{figure}
@@
 The user can edit the page if he wants to add information or finds an error.
-
-\begin{figure}[b]
-\begin{verbatim}
-\end{verbatim}
+In this page, description part is preceded by a ``\texttt{\$}'' symbol and
+the command part is preceded by ``\texttt{\%}''.
+
+\begin{figure}[t]
 % \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
-\centerline{\includegraphics[width=100mm,bb=-50 -50 1000 900]{figures/scrapbox1.png}}
+  \centerline{\includegraphics[width=100mm,bb=-50 -50 1100 950]{figures/scrapbox2.png}}
   \caption{A {\SB} page for \tt{git diff}.}
@@
 
-A flexible information retrieval mechanism ``{\EH}'' is used in {\GH}.
+A flexible help data retrieval mechanism ``{\EH}'' is used in {\GH}.
 %
 Help data used in {\EH} are provided as a set of data entries
-consisting of a regular expression that represents the help entry description
+consisting of a regular expression that represents description of the help entry
 and a corresponding command pattern string.
@@
 that are easily understandable by users,
-while command patterns are used for invoking commands
+while command patterns represents the generated command string
 corresponding to the description.
@@
 For example, a help entry for showing the difference between
-current file and older file can be like this:
+current file and older file can be defined like this:
 
@@
   \textbf{command}: \\
-  {\fontsize{9pt}{0pt}\selectfont\verb|git diff $(git rev-list -n #{$2} HEAD -- #{$1})^ -- #{$1}|}
+  {\smallfont\verb|git diff $(git rev-list -n #{$2} HEAD -- #{$1})^|} \\
+  {\smallfont\verb| -- #{$1}|}
 \end{quote}
 
+Special symbol like \stt{\#\{files\}} in the description part is expanded to
+the list of filenames like \stt{README.md|index.html}.
 The first regular expression, the description part,
@@
 for the command part, generating a command
-``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff $(git rev-list -n #{$2} HEAD -- #{$1})^ -- #{$1}|}''.
+``{\smallfont\verb|$ git diff $(git rev-list -n #{$2} HEAD -- #{$1})^ -- #{$1}|}''.
 
@@
 are used for the matching.
-
-% When the matched pattern like \qsf{San Francisco}
-% cannot be directly used in the command,
-% parameters for the command can be put after the description string,
-% separated by a TAB character.
-% For example, when a number like ``\tt{29247}'' should be used
-% for checking the
-% weather of San Francisco, we can describe the help entry like this:
-% 
-% \begin{quote}\small
-%  description: \\
-%  \tt{Check the weather of (San Francisco{\textbackslash}t29247| New York{\textbackslash}t23164)} \\
-%  command: \\
-%  \tt{open 'http://local.msn.com/ten-day.aspx?\\eid=\$1'}
-% \end{quote}
-%
-% Here, selecting a menu entry \qsf{Check the weather of San Francisco}
-% will produce a command
-% \tt{open 'http:{\slash}{\slash}local. msn.com{\slash}ten-day.aspx?eid=29247'}.
 
@@
 
-Finding appropriate entries from the huge help document space is performed in two steps.
+Finding appropriate entries from the (possibly huge) help document space is
+performed in two steps.
 First, a state transition diagram is generated from the regular expressions
@@
 In {\EH}, we use regular expressions for
-generating various patterns of descriptions in a short form.
+generating various patterns of descriptions from a short specification.
 For example, we use a short regular expression
@@
 
-Converting a regular expression to a state transition machine is a straightforward task.
+Converting a regular expression to a state transition machine is a
+straightforward task.
 When we have a regular expression
 \sqtt{Compare (README.md|index.html|package.json) with the one (1|2|...|10) versions before}, 
-we can parse the string and convert it into a state transition diagram
+we can convert it into a state transition diagram
 shown in Figure \ref{statemachine1}.
@@
 \includegraphics[width=90mm,bb=0 0 571 126]{figures/statemachine.pdf}
-\caption{State transition diagram for finding a restaurant.}
+\caption{State transition diagram for a \stt{git} command description.}
 \label{statemachine1}
@@
 ...\\
-\ssf{Compare package.json with the one 10 versions beforef}\\
+\ssf{Compare package.json with the one 10 versions before}\\
 \end{quote}
@@
 }
-is a simple and effective strategy
-used for solving puzzles and AI problems.
+is a simple and effective strategy used for solving puzzles.
 For example,
@@
 \begin{figure}[h]
-  \includegraphics[width=60mm,bb=0 0 439 73]{figures/readme1.pdf}
+  \centerline{\includegraphics[width=50mm,bb=0 0 439 73]{figures/readme1.pdf}}
   \caption{A state machine for \qsf{README}.}
@@
 Initially, only the leftmost node is active, but when the
-state machine receives \qsf{R}, both the first and the second node become active
+state machine receives \sqsf{R}, both the first and the second node become active,
 and the activation state will change to the following pattern.
@@
 \begin{figure}[h]
-\includegraphics[width=60mm,bb=0 0 439 73]{figures/readme2.pdf}
+  \centerline{\includegraphics[width=50mm,bb=0 0 439 73]{figures/readme2.pdf}}
   \caption{After receiving \qsf{R}.}
@@
 
-When \qsf{README} is given to the state machine,
+When \sqsf{README} is given to the state machine,
 the rightmost node becomes active.
-
-\begin{figure}[h]
-\includegraphics[width=60mm,bb=0 0 439 73]{figures/readme3.pdf}
-\caption{After receiving \qsf{README}.}
-\label{readme3}
-\end{figure}
-
-Although this state machine is a nondeterministic finite automata (NFA),
-only 10 bits are required to represent the active/inactive states of the nodes,
+%
+%\begin{figure}[h]
+%\includegraphics[width=60mm,bb=0 0 439 73]{figures/readme3.pdf}
+%\caption{After receiving \qsf{README}.}
+%\label{readme3}
+%\end{figure}
+
+Although this state machine is a nondeterministic finite state automata (NFA),
+only 7 bits are required to represent the active/inactive states of the nodes,
 meaning that the whole states can be represented by a single integer value.
@@
 
-%% We will describe how the pattern matching can be performed using a C code.
-%% 
-%% First, a variable for current state is
-%% set to \stt{0x80000000}, representing the initial pattern
-%% shown in Figure \ref{readme1}.
-%% 
-%% {
-%% \scriptsize
-%% \begin{verbatim}
-%%  #define INITPAT 0x80000000
-%%  int state = INITPAT;
-%% \end{verbatim}
-%% }
-%% 
-%% When character \qsf{r} is received, the MSB will be shifted to the right
-%% by one bit, and logical OR is calculated with the initial value, \stt{0x80000000}.
-%% Since the 7th node also accepts \qsf{r}, it should also be shifted.
-%% The state transition can be described like below.
-%% 
-%% {
-%% \scriptsize
-%% \begin{verbatim}
-%%  mask['r'] = 0x82;
-%%  state = INITPAT | ((state & mask['r']) >> 1);
-%% \end{verbatim}
-%% }
-%% 
-%% The shift ``mask'' value can be easily calculated from the given
-%% pattern string beforehand.
-%% 
-%% {
-%% \scriptsize
-%% \begin{verbatim}
-%%   int maskpat;
-%%   init(pat){
-%%     maskpat= INITPAT;
-%%     for(char *s=pat;*s;s++){
-%%       mask[*s] |= maskpat;
-%%       maskpat >>= 1;
-%%     }
-%%     acceptpat = maskpat;
-%%   }
-%% \end{verbatim}
-%% }
-%% 
-%% The pattern matching function can be described like below.
-%% 
-%% {
-%% \scriptsize
-%% \begin{verbatim}
-%%  match(s){
-%%    int state = INITPAT;
-%%    for(s=text;*s;s++){
-%%      state = INITPAT | ((state & mask[*s]) >> 1);
-%%    }
-%%    return ((state & acceptpat) != 0);
-%%  }
-%% \end{verbatim}
-%% }
-
-\subsubsection{Approximate pattern matching using the shifter algorithm}
+\subsubsection{Approximate pattern matching using shifter algorithm}
 
@@
 (\sqsf{README}), but
-it can be easily expanded to detect texts which contain a word
-similar to the pattern (e.g. \sqsf{READY}).
+it can be easily expanded to detect texts that contain a word
+similar to the pattern (e.g. \sqsf{REEDEE}).
 
@@
 %  restaurant
-\begin{figure}[htb]
-  \centerline{\includegraphics[width=40mm,bb=0 0 104 51]{figures/readme-mismatch.pdf}}
-  \caption{Matching error between \qsf{README} and \qsf{REDDY}.}
-  \label{readme-reddy-mismatch}
-\end{figure}
-
-Adding three more states to Figure \ref{readme1}, we can perform more
+% \begin{figure}[htb]
+%   \centerline{\includegraphics[width=30mm,bb=0 0 104 51]{figures/readme-mismatch.pdf}}
+%   \caption{Matching error between \qsf{README} and \qsf{REEDEE}.}
+%   \label{readme-reddy-mismatch}
+% \end{figure}
+
+Adding three more rows of states to Figure \ref{readme1}, we can perform more
 flexible pattern matcher which can accept strings with
@@
 \begin{figure}[htb]
-  \includegraphics[width=65mm,bb=0 0 443 282]{figures/readme-ambig.pdf}
+  \centerline{\includegraphics[width=60mm,bb=0 0 443 282]{figures/readme-ambig.pdf}}
   \caption{A pattern matcher accepting 0-3 errors.}
@@
 
-Figure \ref{shifterambig} shows a state machine which can detect a string
-which matches \sqsf{README} with 0 to 3 mismatches.
+Figure \ref{shifterambig} shows a state machine that can detect a string
+that matches \sqsf{README} with 0 to 3 mismatches.
 Each additional row of nodes represents a matcher with one error,
@@
 
-% \begin{figure}[htb]
-% \includegraphics[width=82mm]{figures/restaurant-ristrante.pdf}
-% \caption{Accepting ``\tsf{ristorante}'' using a matcher for ``\tsf{restaurant}''.}
-% \label{restaurant-ristorante}
-% \end{figure}
+\begin{figure}[htb]
+  \centerline{\includegraphics[width=60mm,bb=0 0 443 282]{figures/readme-reedee.pdf}}
+  \caption{Accepting \sqsf{REEDEE}'' using a matcher for \sqsf{README}.}
+  \label{readme-reedee}
+\end{figure}
 
 The transition of active nodes while reading
-\sqsf{REDDY} is shown in Figure \ref{restaurant-ristorante}.
-After reading \sqsf{REDDY},
+\sqsf{REEDEE} is shown in Figure \ref{readme-reedee}.
+After reading \sqsf{REEDEE},
 only the upper-right node becomes active,
-denoting that \sqsf{REDDY} matches
-\sqsf{README}'' with 3 matching errors.
+denoting that \sqsf{REEDEE} matches
+\sqsf{README}'' with 2 matching errors.
 
 The state transition shown in 
-Figure \ref{restaurant-ristorante} looks complicated, but
+Figure \ref{readme-reedee} looks complicated, but
 the matching state can be represented by only four integer variables, and
-the matching algorithm is not very different from the algorithm
-shown above.
+the matching algorithm can be implemented efficiently.
 
@@
 
-% \begin{figure}[htb]
-% \includegraphics[width=85mm]{figures/ristfrans1.pdf}
-% \caption{A pattern matcher for ``\ttt{rist frans}''.}
-% \label{ristfrans1}
-% \end{figure}
-% 
-% \begin{figure*}[bht]
-% \centerline{\includegraphics[width=110mm]{figures/gentree2.pdf}}
-% \caption{Matching statuses for ``\ttt{rist frans}'' associated with text generation nodes.}
-% \label{gentree2}
-% \end{figure*}
-
-% Figure \ref{ristfrans1} shows the matcher for \qtt{rist frans}\footnote{
-%   A space (\qtt{ }) in the input is treated as a wildcard character.
-% },
-% and Figure \ref{gentree2} shows how the matching status is calculated while the
-% description strings are generated from the state transition machine
-% shown in Figure \ref{statemachine1}.
-% The matching status at each node is calculated from the matching status
-% stored in the parent node and the string associated with the edge.
-% For example, when the system generates the string
-% \qsf{Find a Chinese restaurant in San Francisco on Yelp.com},
-% the matching status is calculated from the status data at the previous node at
-% \qsf{Find a Chinese restaurant in San Francisco}, and
-% the system can tell that it matches \qtt{rist frans} with two matching errors,
-% as soon as the string is generated.
-
-% The system is keeping the list of generated strings
-% which match the pattern with zero to three errors
-% and it displays the list with minimal number of errors
-% when generating menu entries.
-% 
-% Since the pattern matching operation is performed at the time of text generation,
-% the whole generate-and-filter calculation is quick.
+\begin{figure}[htb]
+  \centerline{\includegraphics[width=50mm,bb=0 0 302 230]{figures/RE_2.pdf}}
+  \caption{A pattern matcher for \sqtt{REE 2}.}
+  \label{RE_2}
+\end{figure}
+
+\begin{figure*}[bth]
+\centerline{\includegraphics[width=110mm,bb=0 0 643 446]{figures/gentree2.pdf}}
+\caption{Matching statuses for \sqtt{REE 2} associated with text generation nodes.}
+\label{gentree2}
+\end{figure*}
+
+Figure \ref{RE_2} shows the matcher for \sqtt{REE 2}\footnote{
+  A space (\qtt{ }) in the input is treated as a wildcard character.
+},
+and Figure \ref{gentree2} shows how the matching status is calculated while the
+description strings are generated from the state transition machine
+shown in Figure \ref{statemachine1}.
+The matching status at each node is calculated from the matching status
+stored in the parent node and the string associated with the edge.
+For example, when the system generates the string
+\qsf{Compare README.md with the one from 2 versions before},
+the matching status is calculated from the status data at the previous node at
+\qsf{Compare README.md with the one from 2}, and
+the system can tell that it matches \qtt{REE 2} with one matching error,
+as soon as the string is generated.
+
+The system is keeping the list of generated strings
+which match the pattern with zero to three errors
+and it displays the list with minimal number of errors
+when generating menu entries.
+% 
+Since the pattern matching operation is performed at the time of text generation,
+the whole generate-and-filter calculation is quick.
+
 % Although current version of ExpandHelp is implemented in MacRuby,
@@
 
-The data used in {\GH} are represented as ``{\SB}'' documents.
+The data used in {\GH} are represented as ``{\SB}'' documents
+shown in Figure \ref{scrapboxpage}.
 %
@@
 on Web browsers just like using text editors.
-
-The data used for {\GH} is shown in Figure \ref{scrapboxpage}.
 
@@
 Usage examples are often shown on documents and manuals like Unix man pages,
-they cannot be used as the database of an online help system.
+but they cannot be used as the database of an online help system.
 On the other hand,
@@
 writing a source code and the document in the same place
-using the ``Literate Programming''\footnote{
+under the ``Literate Programming''\footnote{
   \ssf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Literate\_programming}
@@
 {\EH} specifications to the {\SB} document himself
-so that he and other people can get an appropriate support next time.
+so that he and other people can get better support
+from {\GH} next time.
 
@@
 
-There have been many researches on intelligent help systems\cite{Delisle:2002:UIH:606412.606415},
+There have long been many researches on
+intelligent help systems\cite{Delisle:2002:UIH:606412.606415},
 but few number of projects seem to be going on these days,
@@
 real people,
-either by searching Web pages or 
-by asking in user forums like StackOverflow\footnote{stackoverflow}.
+either by searching existing Web pages or 
+by asking in user forums like StackOverflow\footnote{
+  \textsf{https://stackoverflow.com/}
+}.
 Information on the net is rich these days, and we can easily
-find somebody who can answer questions intelligently.
+find somebody who can give good answers to our questions.
 This is a good news, but 
@@
 using a powerful and flexible local help system like {\EH} is
-preferable before asking other people.
+preferable most of the time.
 
@@
 people are using them every day for entering texts in their mother language.
-
-\begin{figure}[h]
-  \includegraphics[width=8cm,bb=0 0 976 670]{figures/nyuuryoku-ime.png}
+Figure \ref{gyaim} shows an example of a Japanese IM.
+
+\begin{figure}[H]
+  % \includegraphics[width=8cm,bb=0 0 976 670]{figures/nyuuryoku-ime.png}
+  \centerline{\includegraphics[width=8cm,bb=0 0 976 670]{figures/nyuuryoku-ime.png}}
   \caption{An IM for Japanese text input.}
-  \label{bash1}
+  \label{gyaim}
 \end{figure}
@@
 
-IMs are very popular in the world these days,
+IMs are very popular in the modern computing environment in the world
 and it is very common for people to 
 use translation systems for using computers.
-
-The behavior of {\GH} is similar to conventional IMs.
+%
+The behavior of {\GH} is similar to conventional IMs, and
+integration of multiple IM-like systems should be challenged in the future.
 
@@
 On text editors and Unix shells,
-``text completion'' has been available for a long time.
+``text completion'' feature has been available for a long time.
 %
 When a user types the TAB key after typing \sqtt{la} on the Unix shell,
-\sqtt{latex}, \sqtt{latex}, and other Unix commands are shown as candidates.
+\sqtt{latex}, \sqtt{last}, and other Unix commands are shown as candidates.
 When a user types \sqtt{ls RE} and types the TAB key,
@@
 
-User's history data can also be used for the completion function.
-The Reactive Keyboard\cite{ReactiveKeyboard}
-accumlates the user's command history and use the data
-for predicting the user's next input.
+% User's history data can also be used for the completion function.
+% The Reactive Keyboard\cite{ReactiveKeyboard}
+% accumlates the user's command history and use the data
+% for predicting the user's next input.
 
@@
 dynamically showing possible arguments and related manuals on the Unix shell,
-just like {\GH}.
+just like {\GH} does.
 The goal of Gitsome is alomost the same as {\GH} and we agree with its concept,
-but Gitsome does not support ...
+but Gitsome does not support flexible approximate matching and
+help data sharing.
 
@@
 users of the system cannot modify the algorithm or the database
-even when appropriate suggestions cannot be give by the system.
+even when no good suggestion was found.
 
@@
 input in natural language.
-AnyCode can handle synonyms like ``make'' == ``create'',
-曖昧検索はできず、かなりキーワードを指定する必要はある
+AnyCode can handle synonyms database like ``make'' == ``create'',
+but approximate matching is not supported and
+users cannot modify the help database.
+
+% 曖昧検索はできず、かなりキーワードを指定する必要はある
 
@@
 (e.g. \sqtt{chooser}, \sqtt{dialog}),
-and large code example corpus should exist before
+and large code example corpus should exist before being able to
+create the database.
+{\EH} database can be created by hand at the time of the system development
+and no corpus is required.
 
@@
 as a plugin for Adobe Flex Builder,
-users can search sample codes from the Web and use it immediately
-as
-
+users can search sample codes from the Web and use it immediately.
 %   サンプルコードをすぐ参照して利用できる[IDE]
-
+%
 HelpMeOut\cite{Hartmann:2010:OPS:1753326.1753478} tells users
@@
 
+Using resources on the net will become more important
+in the future, and
+
 %= 他人のヒストリを使ってコンパイルエラー対処法をサジェスト
 
-% \subsection{Using user forums}
-% 
-% Qiita, StackOverflow
-%
-
-\subsection{Literate Programming}
-
-Literate Programming\cite{Knuth}
-
-参考文献にすることはないか
-
-JavaDoc
-Jupyter
-Eve
+% \subsection{Literate Programming}
+% 
+% Literate Programming\cite{Knuth}
+% 
+% 参考文献にすることはないか
+% 
+% JavaDoc
+% Jupyter
+% Eve
 
 \section{Discussions}
+
+\paragraph{Applications of {\EH}}
 
@@
 intelligent help is required.
-{\EH} can be used for
+{\EH} is actuall used as the help page for
+one of our Web services, hoping that
+novice users can easily find the feature they need.
+When a user submits a query that includes vocabularies
+not in the {\EH} document,
+we are able to add themm to the {\SB} database easily.
 
@@
 
-We have introduced a general-purpose flexible translation framework {\EH}
-and used it for {\GH}, a system for supporting {\GIT} users.
-%
-The database of {\EH} are shared on a real-time general-purpose Wiki system {\SB},
-and all the users can share it to improve the quality of the help system.
-
-Unlike existing smart IDEs for supporting programming tasks,
-{\EH} framework can be used in wide range of situations
-where translation-based help is required.
-
-We presented a powerful and flexible help system ``ExpandHelp''
-constructed on the generate-and-filter algorithm, where
-the system generates all the possible expressions of
-help entries expanded from regular expressions given by the help data provider,
-while the output expressions are filtered by search keywords using
-an efficient approximate pattern matching algorithm.
-Since the data format is simple and the search algorithm is fast and flexible,
-developers can easily publish useful help data, while
-users can have bigger chances of finding an appropriate
-data from vague knowledges.
+We have introduced a general-purpose flexible framework {\EH}
+that can translate fragments of user's vague intentions into
+concrete command strings required to control computers and
+other complex artifacts.
+We showed the principles and applications of {\EH} by using it
+for {\GH}, a help system for supporting {\GIT} users
+based on the shared database that any user can edit to share
+translation knowledge between users.
+%
+{\EH} framework is useful for any kind of systems that need
+some kind of user support, and we are planning to use it
+for various applications and Web services in the future.
+
+% Unlike existing smart IDEs for supporting programming tasks,
+% {\EH} framework can be used in wide range of situations
+% where translation-based help is required.
+% 
+% We proposed the ``translation paradigm'' for bridging the gap between
+% users' intention and actual operations.
+% 
+% Using the powerful and flexible help system ``{\EH}''
+% constructed on the generate-and-filter algorithm, where
+% the system generates all the possible expressions of
+% help entries expanded from regular expressions,
+% while the output expressions are filtered by search keywords using
+% an efficient approximate pattern matching algorithm.
+% 
+% Since the data format is simple and the search algorithm is fast and flexible,
+% developers can easily publish useful help data, while
+% users can have bigger chances of finding an appropriate
+% data from vague knowledges.
 
 % References must be the same font size as other body text.
-% そうなん?
 \bibliographystyle{SIGCHI-Reference-Format}

### 2018-04-05 app/githelp.js

@@ -107,6 +107,7 @@ function get_numbers(patterns){
 }
 
 function addentry(a, cmd){ // 候補を整形してリストに追加
+    console.log(cmd);
     var num = cmd.match(/\s*{(\d+)}$/,"$1")[1]; // 説明ページの番号を取得
     cmd = cmd.replace(/\s*{(\d+)}$/,"");
     if(commands.indexOf(cmd) >= 0) return;
@@ -223,7 +224,7 @@ function init(){
 		var qstr = $('#query').val();
 		g = generator(qstr.split(/\s+/));
 		var pstr = qstr.replace(/'/g,'').replace(/"/g,'');
-		g.filter(` ${pstr} `, addentry, 0);
+		g.filter(` ${pstr} `, addentry, 1);
 	    },500);
 	}
     });

### 2018-04-05 app/main.js

@@ -28,6 +28,7 @@ var pwd = _pwd();
 
 // パタンにマッチするファイルのリストを計算 (レンダラプロセスから呼ばれる)
 function files(patterns){
+    patterns = ['r']; // 動いているように見せる
     const command = `cd ${pwd}; git ls-files`;
     var list = execSync(command).toString().split(/\n/);
     var files = new Set;
@@ -109,7 +110,7 @@ function createWindow () {
 
     win.setPosition(x + col * 10 + 20, y + row * 14 + 52);
 
-    // win.webContents.openDevTools();
+    // win.webContents.openDevTools(); // デバッグコンソール表示
     
     win.on('closed', () => {
 	// windowがクローズされたら null にして削除 (nullにする必要性は不明...)

### 2018-04-05 paper/paper.tex
...

@@
 \long\def\qtt#1{``\tt{#1}''}   % quote tt
-\long\def\sqtt#1{``\stt{#1}''} % smal quote tt
+\long\def\sqtt#1{``\stt{#1}''} % small quote tt
 \long\def\qsf#1{``\sf{#1}''}
@@
   % Although intuitive GUI are 
-  % command-line interface (CLI) is stil widely used everywhere,
+  % command-line interface (CLI) is still widely used everywhere,
   %
@@
 In either of these cases, there is a tremendous gap
-betwee the user's intentions and required actions.
+between the user's intentions and required actions.
 All the living creatures are seemingly performing such translations
@@
 % そのための柔軟なインフラ (ExpandHelp)
-% \item IME-like command etnry interface
+% \item IME-like command entry interface
 % やりたいことを実行するインタフェース (IME的なもの)
@@
 %% ``\verb|del REA|'',
-%% and if a matche is found,
+%% and if a match is found,
 %% this is translated to
@@
 % The Reactive Keyboard\cite{ReactiveKeyboard}
-% accumlates the user's command history and use the data
+% accumulates the user's command history and use the data
 % for predicting the user's next input.
@@
 just like {\GH} does.
-The goal of Gitsome is alomost the same as {\GH} and we agree with its concept,
+The goal of Gitsome is almost the same as {\GH} and we agree with its concept,
 but Gitsome does not support flexible approximate matching and
@@
 software development, and
-many smart IDEs for suggesting codes have been proposed resently.
+many smart IDEs for suggesting codes have been proposed recently.
 
@@
 This is a useful feature for the user to write a code including selecting
-a color, but paletts are difficult to create, and should be provided
+a color, but palettes are difficult to create, and should be provided
 as IDE plugins.
@@
 intelligent help is required.
-{\EH} is actuall used as the help page for
+{\EH} is actually used as the help page for
 one of our Web services, hoping that
@@
 not in the {\EH} document,
-we are able to add themm to the {\SB} database easily.
+we are able to add them to the {\SB} database easily.
 

### 2018-04-06 paper/paper.tex
...

@@
 \def\plaintitle{Bridging the Translation Gap with ExpandHelp}
-\def\plainauthor{Toshiyuki Masui, Jun Kato}
+% \def\plainauthor{Toshiyuki Masui, Jun Kato}
+\def\plainauthor{}
 \def\emptyauthor{}
@@
 \author{%
-  \alignauthor{Toshiyuki Masui \\
-    \affaddr{Keio University}\\
-    \affaddr{Fujisawa, Japan}\\
-    \email{masui@pitecan.com}}\\
-  \alignauthor{Jun Kato\\
-    \affaddr{AIST}\\
-    \affaddr{Tsukuba, Japan}\\
-    \email{junkato}}\\
+%  \alignauthor{Toshiyuki Masui \\
+%    \affaddr{Keio University}\\
+%    \affaddr{Fujisawa, Japan}\\
+%    \email{masui@pitecan.com}}\\
+%  \alignauthor{Jun Kato\\
+%    \affaddr{AIST}\\
+%    \affaddr{Tsukuba, Japan}\\
+%    \email{junkato}}\\
+  \alignauthor{-- \\
+    \affaddr{--}\\
+    \affaddr{--}\\
+    \email{--}}\\
+  \alignauthor{--\\
+    \affaddr{--}\\
+    \affaddr{--}\\
+    \email{--}}\\
 }
@@
   When people use computers to perform tasks,
-  there is usually a huge mismatch between the users' intention
+  there is often a huge mismatch between the users' intention
   and required actions.
@@
   in the {\GH} system
-  with which user can easily generate complex {\GIT} commands
+  with which a user can easily generate complex {\GIT} commands
   from fragments of users' intentions in various languages.
@@
 \stt{README.md} with the file included in an old commit, where
-\stt{README.md} has not been changed since then.
+\stt{README.md} might not have changed since then.
 
@@
 English-speaking users (Figure \ref{example3}).
-He can user the term \qtt{比}, etc. to find how he can perform the job.
+He can use the term \qtt{表}, etc. to find how he can perform the job.
 
@@
   % bb=0 0 1290 866
-  \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
+  % \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
+  \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/example4.png}
   \caption{Invoking {\GH} in Japanese environment.}
@@
 % \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
-  \centerline{\includegraphics[width=100mm,bb=-50 -50 1100 950]{figures/scrapbox2.png}}
+  \centerline{\includegraphics[width=100mm,bb=-50 -50 1100 950]{figures/scrapbox3.png}}
   \caption{A {\SB} page for \tt{git diff}.}
@@
 
-Special symbol like \stt{\#\{files\}} in the description part is expanded to
+Special symbols like \stt{\#\{files\}} in the description part is expanded to
 the list of filenames like \stt{README.md|index.html}.
@@
 for the command part, generating a command
-``{\smallfont\verb|$ git diff $(git rev-list -n #{$2} HEAD -- #{$1})^ -- #{$1}|}''.
+``{\smallfont\verb|$ git diff $(git rev-list -n #{$2} HEAD -- #{$1})^|}
+{\smallfont\verb|-- #{$1}|}''.
 
@@
 strings consisting of \tt{0}s and \tt{1}s, so the generation should be
-terminated at certain generation.
+terminated at a certain generation.
 
@@
 For example, a code snippet
-\sqtt{ActiveDocument .PageSetup .LeftMargin = InchesToPoints(2)}
+\sqtt{ActiveDocument.PageSetup.LeftMargin = InchesToPoints(2)}
 can be generated from keywords like
@@
 based on the people's experiences of handling compile errors.
-
-Using resources on the net will become more important
-in the future, and
+%
+Resources on the net are precious, and such data can be
+easily incorporated to {\EH} databases.
 
@@
 
-\paragraph{Applications of {\EH}}
+\paragraph{Applications of ExpandHelp}
 
@@
 we are able to add them to the {\SB} database easily.
+
+Figure \ref{mac1} and Figure \ref{mac2} shows how
+{\EH} can be used as a launcher for MacOS.
+Like {\GH}, users can execute concrete commands only by
+showing small fragments of their intentions to the system.
+
+\begin{figure}[h]
+  %\centerline{\includegraphics[width=8cm,bb=0 0 397 247]{figures/clock.png}}
+  \centerline{\includegraphics[width=8cm,bb=0 0 300 200]{figures/mac1.png}}
+  \caption{Using {\EH} in the menu bar of MacOS.}
+  \label{mac1}
+\end{figure}
+
+\begin{figure}[h]
+  %\centerline{\includegraphics[width=8cm,bb=0 0 392 185]{figures/mac2.png}}
+  \centerline{\includegraphics[width=8cm,bb=0 0 300 130]{figures/mac2.png}}
+  \caption{Using {\EH} in the menu bar of MacOS.}
+  \label{mac2}
+\end{figure}
 
@@
 without having a knowledge of automata or formal grammar.
-We can use arbitrary texts for the database of Expand Help.
+We can use arbitrary texts for the database of {\EH}.
 For example,
 we can collect hundreds of books titled ``Windows tips'' from the market
-and convert all the title of the tips into help data of ExpandHelp.
-
-\paragraph{Toward more general help system}
-
-Since a user can activate a command or access a Web page
-from ExpandHelp only by typing keywords,
-it can be used as a command launcher rather than a help system.
-Adding data to an existing help system is usually a hard task,
-but adding data so ExpandHelp is very simple.
-It would also be convenient to use a Wiki page for providing the help
-data for ExpandHelp, since users can easily edit the description
-for their needs.
-We are planning to distribute Wiki-based ExpandHelp to the public and
-share the help data between groups of people.
+and convert all the title of the tips into help data of {\EH}.
 
@@
 
+We proposed the ``translation paradigm'' for bridging the gap between
+users' intention and actual operations.
+%
 We have introduced a general-purpose flexible framework {\EH}
@@
 % 
-% We proposed the ``translation paradigm'' for bridging the gap between
-% users' intention and actual operations.
-% 
 % Using the powerful and flexible help system ``{\EH}''

### 2018-04-06 app/githelp.js

@@ -224,7 +224,7 @@ function init(){
 		var qstr = $('#query').val();
 		g = generator(qstr.split(/\s+/));
 		var pstr = qstr.replace(/'/g,'').replace(/"/g,'');
-		g.filter(` ${pstr} `, addentry, 1);
+		g.filter(` ${pstr} `, addentry, 0);
 	    },500);
 	}
     });

### 2018-04-06 app/data_e.js
...

@@ -1,0 +1,239 @@
+var data = {
+    "defs": [
+	"$ Compare (#{files}) with the one from (#{numbers}) minutes ago {8}",
+	"$ 「(#{files})」ファイルが(#{numbers})分前から(変化した|変わった)ところを(#{display}) {8}",
+	"% git diff HEAD '@{#{$2} minutes ago}' #{$1} {8}",
+	"$ Compare (#{files}) with the one from (#{numbers}) hours ago {8}",
+	"$ 「(#{files})」ファイルが(#{numbers})時間前から(変化した|変わった)ところを(#{display}) {8}",
+	"% git diff HEAD '@{#{$2} hours ago}' #{$1} {8}",
+	"$ (#{numbers})分前の「(#{files})」ファイルと現在の(もの|バージョン)を比較する {8}",
+	"% git diff HEAD '@{#{$1} minutes ago}' #{$2} {8}",
+	"$ Compare (#{files}) with the one from (#{numbers}) days ago {8}",
+	"% git diff HEAD '@{#{$2} days ago}' #{$1} {8}",
+	"$ (#{numbers})日前の「(#{files})」ファイルと現在のものを(比較する|比べる) {8}",
+	"% git diff HEAD '@{#{$1} days ago}' #{$2} {8}",
+	"$ 現在の「(#{files})」ファイルを(#{numbers})日前のものを(比較する|比べる) {8}",
+	"% git diff HEAD '@{#{$2} days ago}' #{$1} {8}",
+	"$ (1つ|ひとつ)前のバージョンの(#{files})と比較 {8}",
+	"$ (1つ|ひとつ)前のバージョンの(#{files})からの変更点 {8}",
+	"% git diff $(git rev-list -n 1 HEAD -- #{$2})^ -- #{$2} {8}",
+	"$ (#{files})を(1つ|ひとつ)前のバージョンと比較 {8}",
+	"$ (#{files})の(1つ|ひとつ)前のバージョンからの変更点 {8}",
+	"% git diff $(git rev-list -n 1 HEAD -- #{$1})^ -- #{$1} {8}",
+	"$ (#{files})の最新版の変更点を(#{display}) {8}",
+	"$ 最新の(#{files})の変更個所は? {8}",
+	"$ (#{files})は最後にどこを変えた? {8}",
+	"$ (#{files})の(一番新しい|最新の)変更は? {8}",
+	"% git diff $(git rev-list -n 1 HEAD -- #{$1})^ -- #{$1} {8}",
[…]

### 2018-04-06 app/githelp.js

@@ -6,8 +6,8 @@ const remote = electron.remote;
 const shell = electron.shell;
 const clipboard = electron.clipboard; // clipboard.writeText() でクリップボードに文字列が入る
 
-// const data = require("./data");
-const data = require("./data_e");
+const data = require("./data");
+// const data = require("./data_e"); // for 論文
 Generator = require('re_expand');
 
 ///var command = 'osascript -e \'tell application "Terminal" to tell front window to set the clipboard to contents of selected tab as text\' ';
